---
title: "Appendix 2a:" 
subtitle: "Center for Disease Control and Prevention (CDC) Analysis Results"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## load packages
require(readxl)
require(data.table)
require(tidyverse)
require(dplyr)
require(car)
require(lmtest)
require(sandwich)
require(psych)
require(tseries)
require(fUnitRoots)
require(urca)
require(TSA)
require(forecast)
require(ggplot2)
require(ggthemes)
require(corrplot)
require(sjPlot)
require(gridExtra)
```


```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# read in data files
# Compressed Mortality CDC 1968-2016
cdc <- read_excel("/Data/CDC_film_6816_rates.xlsx")

# number of deaths by year
by_yr <- read_excel("/Data/CDC_deaths_by_YR.xlsx")
```

### Section 1
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# df set
# vars and correlation
cdc_cor <- cdc[,c(1,8:11,14:16,21)]

# rename vars
cdc_cor <- cdc_cor[,1:8] %>%
  rename(`Single Act` = single_rate,
         `Multiple Acts` = multiple_rate,
         `Single Act w/G` = single_rate_gun,
         `Multiple Acts w/G` = multiple_rate_gun,
         `FA Weapons Ban` = `FAWB (tighten)`,
         `Major US Military Involvement` = `Major military involvement`)

# aggregate and get means 
cdc_cor <- aggregate(subset(cdc_cor, sel = -Year), list(year = cdc_cor$Year), mean, na.rm=T)
cdc_cor <- cdc_cor %>%
  rename(Year =year)

# add yearly deaths
deaths <- by_yr[,1:2] %>%
  rename(`Deaths per Year` = Deaths)

# merge in deaths Over Time
cdc_cor <- merge(cdc_cor,deaths, by= "Year")
cdc_core <- cdc_cor

# make into ts object
cdc_cor_ts <- ts(cdc_cor)
```

### Descriptive Statistics
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# correlations and visualizations
# descriptives
tab_df(describe(cdc_cor_ts),
  title = "Centers for Disease Control",
  show.rownames = TRUE)
```

### Correlations
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# create a cdc correlation matrix
cdc_cor_matrix <- cor(cdc_cor_ts, use = "complete.obs")
tab_corr(cdc_cor_matrix)
```

### Visualizations
### Correlation Table
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# create a cdc correlation plot
corrplot(cdc_cor_matrix[c(1:5,9),c(1:5,9)], method = "number",number.cex = 0.9, tl.col = "black", tl.cex = 0.95, tl.offset = 0.2)
```

### Independent and Dependent Variable Time Trends   
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# cdc objects for gg plot
# Single Act
cdc_single <- cdc_core %>%
  group_by(Year,`Single Act`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Multiple Act
cdc_multi <- cdc_core %>%
  group_by(Year,`Multiple Acts`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Single Act w/Gun
cdc_single_gun <- cdc_core %>%
  group_by(Year,`Single Act w/G`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Multiple Act w/Gun
cdc_multi_gun <- cdc_core %>%
  group_by(Year,`Multiple Acts w/G`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()
```


```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# cdc movie ggplots
# Single Act
cdc_sing <- ggplot(data = cdc_single, aes(x = Year, y = `Single Act`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with a Single Modeled Act \nof Violence Over Time",
       subtitle = "Modeled Act w/o Firearm",
       x = "Year",
       y = "Single Modeled Act of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Multiple Act
cdc_multi <- ggplot(data = cdc_multi, aes(x = Year, y = `Multiple Acts`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with Multiple Modeled Acts \nof Violence Over Time",
       subtitle = "Modeled Acts w/o Firearms",
       x = "Year",
       y = "Multiple Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
   # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))
  

# Single Act w/Gun
cdc_sing_gun <- ggplot(data = cdc_single_gun, aes(x = Year, y = `Single Act w/G`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with a Single Modeled Act \nof Violence Over Time",
       subtitle = "Modeled Act w/ Firearm",
       x = "Year",
       y = "Single Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
   # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Multiple Act w/Gun
cdc_multi_gun <- ggplot(data = cdc_multi_gun, aes(x = Year, y = `Multiple Acts w/G`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with Multiple Modeled Acts \nof Violence Over Time",
       subtitle = "Modeled Acts w/ At Least One Firearm Instance",
       x = "Year",
       y = "Multiple Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
   # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))
```

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# cdc mortality ggplots
# Homicide and Assault deaths Over Time 
cdc_death_per_yr <- ggplot(data = cdc_core, aes(x = Year, y = `Deaths per Year`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Homicide and Assault Deaths Over Time",
       x = "Year",
       y = "Number of Homicide and Assault Deaths") +
  theme_tufte() +
   # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# cdc Homicide and Assaults death Over Time LOG
cdc_death_per_yr_log <- ggplot(data = cdc_core, aes(x = Year, y = log(`Deaths per Year`))) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Homicide and Assault Deaths Over Time (LOG)",
       x = "Year",
       y = "Homicide and Assault Deaths (LOG)") +
  theme_tufte() +
   # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))
```

##   
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# visualization of ggplots (call gg objects)
# cdc movie rates plots
# cdc_sing
# cdc_multi
# cdc_sing_gun
# cdc_multi_gun
grid.arrange(cdc_sing,cdc_multi,cdc_sing_gun,cdc_multi_gun)
```

## 
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# cdc yearly assault injury counts plots
#cdc_death_per_yr

# cdc yearly assault injury counts LOG plots
#cdc_death_per_yr_log
grid.arrange(cdc_death_per_yr,cdc_death_per_yr_log, ncol = 2)
```

### Section 2
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
```

### Test First regression for AR and UR    
Base linear model with prime variables of interest:   
*Multiple Acts w/G* (IV) and *Deaths per Year* (DV)  
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# new df for lm
cdc_lm <- cdc_core
cdc_lm.ts <- ts(cdc_lm)

# LM Regression
# perform a dms_multi naive regression
cdc_model <- lm(`Deaths per Year` ~ `Multiple Acts w/G` + Year, data = cdc_lm)

# print the summary of the model
tab_model(cdc_model)

```

### Test for autocorrelation in the errors  
em = residuals from the base linear model  
Lag <= 4  
Seems AR4 is present.  

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# check for AR 
# residuals
em <- cdc_model$resid
#min(em)
#max(em)
acf(em,xlim =c(0,10), col = "red", lwd =2)
pacf(em,xlim =c(0,10), col = "red", lwd =2)
plot(em)

# durbin-watson test auto* correlation (strongest evidence for AR4)
dwt(cdc_model, max.lag = 5)
durbinWatsonTest(cdc_model, max.lag=5)

# breusch-Godfrey test serial* correlation AR PRESENT
bgtest(cdc_model)
```

### Test for unit roots  
Seems UR is present  
Adding drift or trend (p<0.05)  
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
##### CHECK FOR UNIT ROOTS #### seems like there is UR
# Dickey-Fuller
# augmented Dickey-Fuller test
adfTest(cdc_lm.ts[,"Deaths per Year"], lags = 0)
adfTest(cdc_lm.ts[,"Deaths per Year"], lags = 1)
# augmented Dickey-Fuller w/ DRIFT
adfTest(cdc_lm.ts[,"Deaths per Year"], lags = 0,type="c")
# augmented Dickey-Fuller w/ TREND
adfTest(cdc_lm.ts[,"Deaths per Year"], lags = 0,type="ct")

#  Dickey-Fuller test unit root
summary(ur.df(cdc_lm.ts[,"Deaths per Year"], lags = 0, type="trend"))
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# set function
# First differencing function from QMSS package
firstD <- function(var, group, df){
  bad <- (missing(group) & !missing(df))
  if (bad) stop("if df is specified then group must also be specified")

  fD <- function(j){ c(NA, diff(j)) }

  var.is.alone <- missing(group) & missing(df)

  if (var.is.alone) {
    return(fD(var))
    }
  if (missing(df)){
    V <- var
    G <- group }
  else{
    V <- df[, deparse(substitute(var))]
    G <- df[, deparse(substitute(group))]
  }

  G <- list(G)
  D.var <- by(V, G, fD)
  unlist(D.var)
  }
```

### Section 3
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# set df
# get first differences for vars
cdc_lm_FD <- cdc_lm %>%
  summarise(Year = Year,
            `Single Act FD` = firstD(cdc_lm[,"Single Act"]),
            `Multiple Acts FD` = firstD(cdc_lm[,"Multiple Acts"]),
            `Single Act w/G FD` = firstD(cdc_lm[,"Single Act w/G"]),
            `Multiple Acts w/G FD` = firstD(cdc_lm[,"Multiple Acts w/G"]),
            `Deaths per Year FD` = firstD(cdc_lm[,"Deaths per Year"]),
            `GDP in Billions FD` = firstD(cdc_lm[,"GDP in Billions"]),
            `FA Weapons Ban FD` = firstD(cdc_lm[,"FA Weapons Ban"]),
            `Major US Military Involvement FD` = firstD(cdc_lm[,"Major US Military Involvement"]))

# merge by "Year"
cdc_lm_Total <- merge(cdc_lm,cdc_lm_FD, by = "Year")

# convert to ts objects
cdc_lm_TFD.ts <- ts(cdc_lm_Total)
```

### Multiple Modelings with at least one incident with GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# Deaths Over Time First Differences
# LM Regression
# perform a sas naive regression w/ time trend var
cdc_model <- lm(`Deaths per Year FD` ~ `Multiple Acts w/G FD` + Year, data = cdc_lm_Total)

# perform some cdc multiple regressions
cdc_cntrl1 <- lm(`Deaths per Year FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD`, data = cdc_lm_Total)

cdc_cntrl2 <- lm(`Deaths per Year FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = cdc_lm_Total)
cdc_cntrl3 <- lm(`Deaths per Year FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = cdc_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(cdc_model)
summary(cdc_cntrl1)
summary(cdc_cntrl2)
summary(cdc_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# Model Table
models <- list(cdc_model,cdc_cntrl1,cdc_cntrl2,cdc_cntrl3)
       
tab_model(models,show.ci = FALSE)
```


### Multiple Modeling incidents NO GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# Deaths Over Time First Differences
# LM Regression
# perform a sas naive regression w/ time trend var
cdc_model <- lm(`Deaths per Year FD` ~ `Multiple Acts FD` + Year, data = cdc_lm_Total)

# perform some cdc multiple regressions
cdc_cntrl1 <- lm(`Deaths per Year FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD`, data = cdc_lm_Total)

cdc_cntrl2 <- lm(`Deaths per Year FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = cdc_lm_Total)
cdc_cntrl3 <- lm(`Deaths per Year FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = cdc_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(cdc_model)
summary(cdc_cntrl1)
summary(cdc_cntrl2)
summary(cdc_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# Model Table
models <- list(cdc_model,cdc_cntrl1,cdc_cntrl2,cdc_cntrl3)
       
tab_model(models,show.ci = FALSE)
```


### Single Modeling incident with GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# Deaths Over Time First Differences
# LM Regression
# perform a sas naive regression w/ time trend var
cdc_model <- lm(`Deaths per Year FD` ~ `Single Act w/G FD` + Year, data = cdc_lm_Total)

# perform some cdc multiple regressions
cdc_cntrl1 <- lm(`Deaths per Year FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD`, data = cdc_lm_Total)

cdc_cntrl2 <- lm(`Deaths per Year FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = cdc_lm_Total)
cdc_cntrl3 <- lm(`Deaths per Year FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = cdc_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(cdc_model)
summary(cdc_cntrl1)
summary(cdc_cntrl2)
summary(cdc_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# Model Table
models <- list(cdc_model,cdc_cntrl1,cdc_cntrl2,cdc_cntrl3)
       
tab_model(models,show.ci = FALSE)
```


### Single Modeling incident NO GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# Deaths Over Time First Differences
# LM Regression
# perform a sas naive regression w/ time trend var
cdc_model <- lm(`Deaths per Year FD` ~ `Single Act FD` + Year, data = cdc_lm_Total)

# perform some cdc_multi multiple regressions
cdc_cntrl1 <- lm(`Deaths per Year FD` ~ `Single Act FD` + Year + `GDP in Billions FD`, data = cdc_lm_Total)

cdc_cntrl2 <- lm(`Deaths per Year FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = cdc_lm_Total)
cdc_cntrl3 <- lm(`Deaths per Year FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = cdc_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(cdc_model)
summary(cdc_cntrl1)
summary(cdc_cntrl2)
summary(cdc_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# CDC
# Model Table
models <- list(cdc_model,cdc_cntrl1,cdc_cntrl2,cdc_cntrl3)
       
tab_model(models,show.ci = FALSE)
```