---
title: "Appendix 2b:" 
subtitle: "Firearm Injury Surveilance (FIS) Analysis Results"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## load packages
require(readxl)
require(data.table)
require(tidyverse)
require(dplyr)
require(car)
require(lmtest)
require(sandwich)
require(psych)
require(tseries)
require(fUnitRoots)
require(urca)
require(TSA)
require(forecast)
require(ggplot2)
require(ggthemes)
require(corrplot)
require(sjPlot)
require(gridExtra)
```


```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# FIS
# read in .tsv data files
# Firearm Injury Surveillance Study 1993-2018
fis <- read.table("/Data/FIS_film_9320_rates.tsv",header=TRUE, sep="\t")
```

### Section 1   
```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# FIS
# df set
# vars and correlation
fis_core <- fis[,c(1,8:11,14:16,35:37)]

#rename vars
fis_core <- fis_core %>%
  rename(`Single Act` = single_rate,
         `Multiple Acts` = multiple_rate,
         `Single Act w/G` = single_rate_gun,
         `Multiple Acts w/G` = multiple_rate_gun,
         `Assault Injuries` = assaults_per_yr,
         `Gun Injuries` = gunshot_wounds_per_yr,
         `Gun Injuries/Assault` = gunshot_assault_ratio,
         `GDP in Billions` = GDP.in.Billions,
         `FA Weapons Ban` = FAWB..tighten.,
         `Major US Military Involvement` = Major.military.involvement)

# aggregate and get means
fis_core <- aggregate(subset(fis_core, sel = -Year), list(year = fis_core$Year), mean, na.rm=T)
fis_core <- fis_core %>%
  rename(Year = year)

# make into ts object
fis_core_ts <- fis_core
```

### Descriptive Statistics  
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# correlations and visualizations
# descriptives
tab_df(describe(fis_core_ts),
  title = "Firearm Injury Surveillance",
  show.rownames = TRUE)
```

### Correlations  
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# create a fis correlation matrix
fis_core_matrix <- cor(fis_core_ts, use = "complete.obs")
tab_corr(fis_core_matrix)
```

### Visualizations  
### Correlation Table  
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# create a fis correlation plot
corrplot(fis_core_matrix[c(1:5,9:11),c(1:5,9:11)], method = "number",number.cex = 0.8, tl.col = "black", tl.cex = 0.95, tl.offset = 0.2)
```

### Independent and Dependent Variable Time Trends 
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# fis objects for gg plot
# Single Act
fis_single <- fis_core %>%
  group_by(Year,`Single Act`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Multiple Act
fis_multi <- fis_core %>%
  group_by(Year,`Multiple Acts`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Single Act w/Gun
fis_single_gun <- fis_core %>%
  group_by(Year,`Single Act w/G`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Multiple Act w/Gun
fis_multi_gun <- fis_core %>%
  group_by(Year,`Multiple Acts w/G`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()
```


```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# fis movie ggplots
# Single Act
fis_sing <- ggplot(data = fis_single, aes(x = Year, y = `Single Act`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with a Single Modeled Act \nof Violence Over Time",
       subtitle = "Modeled Act w/o Firearm",
       x = "Year",
       y = "Single Modeled Act of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Multiple Act
fis_multi <- ggplot(data = fis_multi, aes(x = Year, y = `Multiple Acts`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with Multiple Modeled Acts \nof Violence Over Time",
       subtitle = "Modeled Acts w/o Firearms",
       x = "Year",
       y = "Multiple Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Single Act w/Gun
fis_sing_gun <- ggplot(data = fis_single_gun, aes(x = Year, y = `Single Act w/G`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with a Single Modeled Act \nof Violence Over Time",
       subtitle = "Modeled Act w/ Firearm",
       x = "Year",
       y = "Single Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Multiple Act w/Gun
fis_multi_gun <- ggplot(data = fis_multi_gun, aes(x = Year, y = `Multiple Acts w/G`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with Multiple Modeled Acts of \nViolence Over Time",
       subtitle = "Modeled Acts w/ At Least One Firearm Instance",
       x = "Year",
       y = "Multiple Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))
```

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# fis gun injuries ggplots
# Incidents of Assault Injuries
fis_assault_per_yr <- ggplot(data = fis_core, aes(x = Year, y = `Assault Injuries`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Assault Injury Incidents Over Time",
       x = "Year",
       y = "Number of Assault Injury Incidents") +
  theme_tufte() +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Gun Injuries during Assaults 
fis_inj_ass_per_yr <- ggplot(data = fis_core, aes(x = Year, y = `Gun Injuries`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Gun Injuries During Assaults Over Time",
       x = "Year",
       y = "Number of Gun Injuries") +
  theme_tufte() +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Average gun injuries per assault Over Time
fis_gun_inj_per_ass <- ggplot(data = fis_core, aes(x = Year, y = `Gun Injuries/Assault`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7)+
  labs(title = "Average Gun Injuries per Assault Over Time",
       x = "Year",
       y = "Average Gun Injuries per Assault") +
  theme_tufte() +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = -0.4,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# fis gun injuries LOG ggplots
# Incidents of Assault Injuries (LOG)
fis_assault_per_yr_log <- ggplot(data = fis_core, aes(x = Year, y = log(`Assault Injuries`))) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Assault Injuries Incidents Over Time (LOG)",
       x = "Year",
       y = "Number of Assault Injury Incidents (LOG)") +
  theme_tufte() +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Incidents of Gun Injuries during Assaults (LOG)
fis_inj_ass_per_yr_log <- ggplot(data = fis_core, aes(x = Year, y = log(`Gun Injuries`))) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Gun Injuries During Assaults Over Time (LOG)",
       x = "Year",
       y = "Number of Gun Injuries (LOG)") +
  theme_tufte() +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Average gun injuries per assault injuries Over Time (LOG)
fis_gun_inj_per_ass_log <- ggplot(data = fis_core, aes(x = Year, y = log(`Gun Injuries/Assault`))) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Average Gun Injuries per Assault Over Time (LOG)",
       x = "Year",
       y = "Average Gun Injuries per Assault (LOG)") +
  theme_tufte() +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = -0.4,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))
```

##   
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE, fig.width = 7.5}
# FIS
# visualization of ggplots (call gg objects)
# fis movie rates plots
# fis_sing
# fis_multi
# fis_sing_gun
# fis_multi_gun
grid.arrange(fis_sing,fis_multi,fis_sing_gun,fis_multi_gun)
```

## 
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE, fig.width = 7.5}
# fis yearly assault injury counts plots
# fis_assault_per_yr
# fis_inj_ass_per_yr
# fis_gun_inj_per_ass
grid.arrange(fis_assault_per_yr,fis_inj_ass_per_yr,fis_gun_inj_per_ass, ncol = 2)

# fis yearly assault injury counts LOG plots
# fis_assault_per_yr_log
# fis_inj_ass_per_yr_log
# fis_gun_inj_per_ass_log
grid.arrange(fis_assault_per_yr_log,fis_inj_ass_per_yr_log,fis_gun_inj_per_ass_log, ncol = 2)
```

### Section 2
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE, fig.width = 7.5}
```


### Test First regression for AR and UR  
Base linear model with prime variables of interest:  
*Multiple Acts w/G* (IV) and *Assault Injuries* (DV)  
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# new df for lm
fis_lm <- fis_core
fis_lm.ts <- ts(fis_lm)

# LM Regression
# perform a fis_multi naive regression
fis_model <- lm(`Assault Injuries` ~ `Multiple Acts w/G` + Year, data = fis_lm)

# print the summary of the model
tab_model(fis_model)

```

### Test for autocorrelation in the errors  
em = residuals from the base linear model  
Lag <= 2  
Seems AR2 is present.

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# check for AR 
# residuals
em <- fis_model$resid
#min(em)
#max(em)
acf(em,xlim =c(0,40), col = "red", lwd =2)
pacf(em,xlim =c(0,40), col = "red", lwd =2)
plot(em)

# durbin-watson test auto* correlation 
dwt(fis_model, max.lag = 2)
durbinWatsonTest(fis_model, max.lag=2)

# breusch-Godfrey test serial* correlation 
bgtest(fis_model)
```

### Test for unit roots  
Seems UR is present  
Adding drift or trend (p>0.05)  
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
##### CHECK FOR UNIT ROOTS #### seems like there is UR
# Dickey-Fuller
# augmented Dickey-Fuller test
adfTest(fis_lm.ts[,"Assault Injuries"], lags = 2)
# augmented Dickey-Fuller w/ DRIFT
adfTest(fis_lm.ts[,"Assault Injuries"], lags = 2,type="c")
# augmented Dickey-Fuller w/ TREND
adfTest(fis_lm.ts[,"Assault Injuries"], lags = 2,type="ct")

#  Dickey-Fuller test unit root
summary(ur.df(fis_lm.ts[,"Assault Injuries"], lags = 2, type="trend"))
```


```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# set function
# First differencing function from QMSS package
firstD <- function(var, group, df){
  bad <- (missing(group) & !missing(df))
  if (bad) stop("if df is specified then group must also be specified")

  fD <- function(j){ c(NA, diff(j)) }

  var.is.alone <- missing(group) & missing(df)

  if (var.is.alone) {
    return(fD(var))
    }
  if (missing(df)){
    V <- var
    G <- group }
  else{
    V <- df[, deparse(substitute(var))]
    G <- df[, deparse(substitute(group))]
  }

  G <- list(G)
  D.var <- by(V, G, fD)
  unlist(D.var)
  }
```

### Section 3
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS 
# set df
# get first differences for vars
fis_lm_FD <- fis_lm %>%
  summarise(Year = Year,
            `Single Act FD` = firstD(fis_lm[,"Single Act"]),
            `Multiple Acts FD` = firstD(fis_lm[,"Multiple Acts"]),
            `Single Act w/G FD` = firstD(fis_lm[,"Single Act w/G"]),
            `Multiple Acts w/G FD` = firstD(fis_lm[,"Multiple Acts w/G"]),
            `Assault FD` = firstD(fis_lm[,"Assault Injuries"]),
            `Gun Injuries FD` = firstD(fis_lm[,"Gun Injuries"]),
            `Gun Injuries/Assault FD` = firstD(fis_lm[,"Gun Injuries/Assault"]),
            `GDP in Billions FD` = firstD(fis_lm[,"GDP in Billions"]),
            `FA Weapons Ban FD` = firstD(fis_lm[,"FA Weapons Ban"]),
            `Major US Military Involvement FD` = firstD(fis_lm[,"Major US Military Involvement"]))

# merge by "Year"
fis_lm_Total <- merge(fis_lm,fis_lm_FD, by = "Year")

# convert to ts objects
fis_lm_TFD.ts <- ts(fis_lm_Total)
```


### Multiple Modelings with at least one incident with GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Assault First Differencing
# LM Regression FD
# perform a fis naive regression w/ time trend var
fis_model <- lm(`Assault FD` ~ `Multiple Acts w/G FD` + Year, data = fis_lm_Total)

# perform some fis multiple regressions
fis_cntrl1 <- lm(`Assault FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD`, data = fis_lm_Total)

fis_cntrl2 <- lm(`Assault FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = fis_lm_Total)
fis_cntrl3 <- lm(`Assault FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = fis_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(fis_model)
summary(fis_cntrl1)
summary(fis_cntrl2)
summary(fis_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Model Table
models <- list(fis_model,fis_cntrl1,fis_cntrl2,fis_cntrl3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Gun Injuries First Differencing
# LM Regression
# perform a fis naive regression w/ time trend var
fis_modelG <- lm(`Gun Injuries FD` ~ `Multiple Acts w/G FD` + Year, data = fis_lm_Total)

# perform some fis multiple regressions
fis_cntrlG1 <- lm(`Gun Injuries FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD`, data = fis_lm_Total)

fis_cntrlG2 <- lm(`Gun Injuries FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = fis_lm_Total)
fis_cntrlG3 <- lm(`Gun Injuries FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = fis_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(fis_modelG)
summary(fis_cntrlG1)
summary(fis_cntrlG2)
summary(fis_cntrlG3)

```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Model Table
models <- list(fis_modelG,fis_cntrlG1,fis_cntrlG2,fis_cntrlG3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Gun Injuries/Assault First Differencing
# LM Regression
# perform a fis naive regression w/ time trend var
fis_modelI <- lm(`Gun Injuries/Assault FD` ~ `Multiple Acts w/G FD` + Year, data = fis_lm_Total)

# perform some fis multiple regressions
fis_cntrlI1 <- lm(`Gun Injuries/Assault FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD`, data = fis_lm_Total)

fis_cntrlI2 <- lm(`Gun Injuries/Assault FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = fis_lm_Total)
fis_cntrlI3 <- lm(`Gun Injuries/Assault FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = fis_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(fis_modelI)
summary(fis_cntrlI1)
summary(fis_cntrlI2)
summary(fis_cntrlI3)

```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Model Table
models <- list(fis_modelI,fis_cntrlI1,fis_cntrlI2,fis_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```


### Multiple Modeling incidents NO GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Assault First Differencing
# LM Regression 
# perform a fis naive regression w/ time trend var
fis_model <- lm(`Assault FD` ~ `Multiple Acts FD` + Year, data = fis_lm_Total)

# perform some fis multiple regressions
fis_cntrl1 <- lm(`Assault FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD`, data = fis_lm_Total)

fis_cntrl2 <- lm(`Assault FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = fis_lm_Total)
fis_cntrl3 <- lm(`Assault FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = fis_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(fis_model)
summary(fis_cntrl1)
summary(fis_cntrl2)
summary(fis_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Model Table
models <- list(fis_model,fis_cntrl1,fis_cntrl2,fis_cntrl3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Gun Injuries First Differencing
# LM Regression 
# perform a fis naive regression w/ time trend var
fis_modelG <- lm(`Gun Injuries FD` ~ `Multiple Acts FD` + Year, data = fis_lm_Total)

# perform some fis multiple regressions
fis_cntrlG1 <- lm(`Gun Injuries FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD`, data = fis_lm_Total)

fis_cntrlG2 <- lm(`Gun Injuries FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = fis_lm_Total)
fis_cntrlG3 <- lm(`Gun Injuries FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = fis_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(fis_modelG)
summary(fis_cntrlG1)
summary(fis_cntrlG2)
summary(fis_cntrlG3)

```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Model Table
models <- list(fis_modelG,fis_cntrlG1,fis_cntrlG2,fis_cntrlG3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Gun Injuries/Assault First Differencing
# LM Regression
# perform a fis naive regression w/ time trend var
fis_modelI <- lm(`Gun Injuries/Assault FD` ~ `Multiple Acts FD` + Year, data = fis_lm_Total)

# perform some fis multiple regressions
fis_cntrlI1 <- lm(`Gun Injuries/Assault FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD`, data = fis_lm_Total)

fis_cntrlI2 <- lm(`Gun Injuries/Assault FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = fis_lm_Total)
fis_cntrlI3 <- lm(`Gun Injuries/Assault FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = fis_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(fis_modelI)
summary(fis_cntrlI1)
summary(fis_cntrlI2)
summary(fis_cntrlI3)

```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Model Table
models <- list(fis_modelI,fis_cntrlI1,fis_cntrlI2,fis_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```


### Single Modeling incident with GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS 
# Assault First Differencing
# LM Regression
# perform a fis naive regression w/ time trend var
fis_model <- lm(`Assault FD` ~ `Single Act w/G FD` + Year, data = fis_lm_Total)

# perform some fis multiple regressions
fis_cntrl1 <- lm(`Assault FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD`, data = fis_lm_Total)

fis_cntrl2 <- lm(`Assault FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = fis_lm_Total)
fis_cntrl3 <- lm(`Assault FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = fis_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(fis_model)
summary(fis_cntrl1)
summary(fis_cntrl2)
summary(fis_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Model Table
models <- list(fis_model,fis_cntrl1,fis_cntrl2,fis_cntrl3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS 
# Gun Injuries First Differences
# LM Regression
# perform a fis naive regression w/ time trend var
fis_modelG <- lm(`Gun Injuries FD` ~ `Single Act w/G FD` + Year, data = fis_lm_Total)

# perform some fis multiple regressions
fis_cntrlG1 <- lm(`Gun Injuries FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD`, data = fis_lm_Total)

fis_cntrlG2 <- lm(`Gun Injuries FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = fis_lm_Total)
fis_cntrlG3 <- lm(`Gun Injuries FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = fis_lm_Total)
```


```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(fis_modelG)
summary(fis_cntrlG1)
summary(fis_cntrlG2)
summary(fis_cntrlG3)

```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Model Table
models <- list(fis_modelG,fis_cntrlG1,fis_cntrlG2,fis_cntrlG3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS 
# Gun Injuries/Assault First Differencing
# LM Regression
# perform a fis naive regression w/ time trend var
fis_modelI <- lm(`Gun Injuries/Assault FD` ~ `Single Act w/G FD` + Year, data = fis_lm_Total)

# perform some fis multiple regressions
fis_cntrlI1 <- lm(`Gun Injuries/Assault FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD`, data = fis_lm_Total)

fis_cntrlI2 <- lm(`Gun Injuries/Assault FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = fis_lm_Total)
fis_cntrlI3 <- lm(`Gun Injuries/Assault FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = fis_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(fis_modelI)
summary(fis_cntrlI1)
summary(fis_cntrlI2)
summary(fis_cntrlI3)

```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Model Table
models <- list(fis_modelI,fis_cntrlI1,fis_cntrlI2,fis_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```


### Single Modeling incident NO GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS 
# Assault First Differencing
# LM Regression 
# perform a fis naive regression w/ time trend var
fis_model <- lm(`Assault FD` ~ `Single Act FD` + Year, data = fis_lm_Total)

# perform some fis multiple regressions
fis_cntrl1 <- lm(`Assault FD` ~ `Single Act FD` + Year + `GDP in Billions FD`, data = fis_lm_Total)

fis_cntrl2 <- lm(`Assault FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = fis_lm_Total)
fis_cntrl3 <- lm(`Assault FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = fis_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(fis_model)
summary(fis_cntrl1)
summary(fis_cntrl2)
summary(fis_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Model Table
models <- list(fis_model,fis_cntrl1,fis_cntrl2,fis_cntrl3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS 
# Gun Injuries First Differencing
# LM Regression
# perform a fis naive regression w/ time trend var
fis_modelG <- lm(`Gun Injuries FD` ~ `Single Act FD` + Year, data = fis_lm_Total)

# perform some fis multiple regressions
fis_cntrlG1 <- lm(`Gun Injuries FD` ~ `Single Act FD` + Year + `GDP in Billions FD`, data = fis_lm_Total)

fis_cntrlG2 <- lm(`Gun Injuries FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = fis_lm_Total)
fis_cntrlG3 <- lm(`Gun Injuries FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = fis_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(fis_modelG)
summary(fis_cntrlG1)
summary(fis_cntrlG2)
summary(fis_cntrlG3)

```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Model Table
models <- list(fis_modelG,fis_cntrlG1,fis_cntrlG2,fis_cntrlG3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS 
# Gun Injuries/Assault First Differencing
# LM Regression
# perform a fis naive regression w/ time trend var
fis_modelI <- lm(`Gun Injuries/Assault FD` ~ `Single Act FD` + Year, data = fis_lm_Total)

# perform some fis multiple regressions
fis_cntrlI1 <- lm(`Gun Injuries/Assault FD` ~ `Single Act FD` + Year + `GDP in Billions FD`, data = fis_lm_Total)

fis_cntrlI2 <- lm(`Gun Injuries/Assault FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = fis_lm_Total)
fis_cntrlI3 <- lm(`Gun Injuries/Assault FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = fis_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(fis_modelI)
summary(fis_cntrlI1)
summary(fis_cntrlI2)
summary(fis_cntrlI3)

```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# FIS
# Model Table
models <- list(fis_modelI,fis_cntrlI1,fis_cntrlI2,fis_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```