---
title: "Appendix 1b:"
subtitle: "Gun Violence Archive (GVA) Analysis Results"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## load packages
require(readxl)
require(data.table)
require(tidyverse)
require(dplyr)
require(car)
require(lmtest)
require(sandwich)
require(psych)
require(tseries)
require(fUnitRoots)
require(urca)
require(TSA)
require(forecast)
require(ggplot2)
require(ggthemes)
require(corrplot)
require(sjPlot)
require(gridExtra)
```


```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# read in .tsv data files
# Gun Violence Archive 2012-2021
gva <- read.table("/Data/GVA_film_1221_rates.tsv",header=TRUE, sep="\t")
```

### Section 1
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# df set
# vars and correlation
gva_cor <- gva[,c(1,10:12,17:23)] %>%
  subset(Year>= 2014)

head(gva_cor)

# rename vars
gva_cor <- gva_cor %>%
  rename(`Single Act` = single_rate,
         `Multiple Acts` = multiple_rate,
         `Single Act w/G` = single_rate_gun,
         `Multiple Acts w/G` = multiple_rate_gun,
         `GDP in Billions` = GDP.in.Billions,
         `FA Weapons Ban` = FAWB..tighten.,
         `Major US Military Involvement` = Major.military.involvement,
         Incidents = incidents_per_yr,
         Fatalities = fatalities_per_yr,
         Injuries = injuries_per_yr)

# aggregate and get means 
gva_cor <- aggregate(subset(gva_cor, sel = -Year), list(year = gva_cor$Year), mean, na.rm=T)
gva_cor <- gva_cor %>%
  rename(Year = year) %>%
   mutate(`Fatalities/Shooting` = Fatalities/Incidents,
          `Injuries/Shooting` = Injuries/Incidents)

# df for later
gva_core <- gva_cor 

# make into ts object
gva_cor_ts <- ts(gva_cor)
```

### Descriptive Statistics
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE,results='asis'}
# GVA
# correlations and visualizations
# descriptives
tab_df(describe(gva_cor_ts),
  title = "Gun Violence Archive",
  show.rownames = TRUE)
```

### Correlations
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE,results='asis'}
# create a gva correlation matrix
gva_cor_matrix <- cor(gva_cor_ts, use = "complete.obs")
tab_corr(gva_cor_matrix)
```

### Visualizations
### Correlation Table
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE,results='asis'}
# create a gva correlation plot
corrplot(gva_cor_matrix[c(1,5:13),c(1,5:13)], method = "number",number.cex = 0.7, tl.col = "black", tl.cex = 0.95, tl.offset = 0.2)
```

### Independent and Dependent Variable Time Trends 
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# gva objects for gg plot
# Single Act
gva_single <- gva_core %>%
  group_by(Year,`Single Act`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Multiple Act
gva_multi <- gva_core %>%
  group_by(Year,`Multiple Acts`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Single Act w/Gun
gva_single_gun <- gva_core %>%
  group_by(Year,`Single Act w/G`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Multiple Act w/Gun
gva_multi_gun <- gva_core %>%
  group_by(Year,`Multiple Acts w/G`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()
```


```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# gva movie ggplots
# Single Act
gva_sing <- ggplot(data = gva_single, aes(x = Year, y = `Single Act`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with a Single Modeled Act \nof Violence Over Time",
       subtitle = "Modeled Act w/o Firearm",
       x = "Year",
       y = "Single Modeled Act of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Multiple Act
gva_multi <- ggplot(data = gva_multi, aes(x = Year, y = `Multiple Acts`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with Multiple Modeled Acts \nof Violence Over Time",
       subtitle = "Modeled Acts w/o Firearms",
       x = "Year",
       y = "Multiple Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Single Act w/Gun
gva_sing_gun <- ggplot(data = gva_single_gun, aes(x = Year, y = `Single Act w/G`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with a Single Modeled Act \nof Violence Over Time",
       subtitle = "Modeled Act w/ Firearm",
       x = "Year",
       y = "Single Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Multiple Act w/Gun
gva_multi_gun <- ggplot(data = gva_multi_gun, aes(x = Year, y = `Multiple Acts w/G`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with Multiple Modeled Acts \nof Violence Over Time",
       subtitle = "Modeled Acts w/ At Least One Firearm Instance",
       x = "Year",
       y = "Multiple Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# gva Shooting Incidents incidents ggplots
# Incidents
gva_incidents_per_yr <- ggplot(data = gva_core, aes(x = Year, y = Incidents)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Shooting Incidents Over Time",
       x = "Year",
       y = "Number of Shooting Incidents") +
  theme_tufte() +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# fatalities during Shooting Incidents
gva_fatalities_per_yr <- ggplot(data = gva_core, aes(x = Year, y = Fatalities)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Fatalities During Shooting Incidents Over Time",
       x = "Year",
       y = "Number of Fatalities During Shooting Incidents") +
  theme_tufte() +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

#injuries during Shooting Incidents
gva_injuries_per_yr <- ggplot(data = gva_core, aes(x = Year, y = Injuries)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Injuries During Shooting Incidents Over Time",
       x = "Year",
       y = "Number of Injuries During Shooting Incidents") +
  theme_tufte() +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Average fatalities per Shooting Incidents
gva_fatalities_per_ms <- ggplot(data = gva_core, aes(x = Year, y = Fatalities/Incidents)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Average Fatalities per Shooting Incidents Over Time",
       x = "Year",
       y = "Average Fatalities per Shooting Incidents") +
  theme_tufte() +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Average injuries per Shooting Incidents
gva_injuries_per_ms <- ggplot(data = gva_core, aes(x = Year, y = Injuries/Incidents)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Average Injuries per Shooting Incidents Over Time",
       x = "Year",
       y = "Average Injuries per Shooting Incidents") +
  theme_tufte() +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))
```


```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# gva gun violence LOG ggplots
# Shooting Incidents (LOG)
gva_incidents_per_yr_log <- ggplot(data = gva_core, aes(x = Year, y = log(Incidents))) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Shooting Incidents Over Time (LOG)",
       x = "Year",
       y = "Number of Shooting Incidents (LOG)") +
  theme_tufte() +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# fatalities during Shooting Incidents (LOG)
gva_fatalities_per_yr_log <- ggplot(data = gva_core, aes(x = Year, y = log(Fatalities))) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Fatalities During Shooting Incidents Over Time (LOG)",
       x = "Year",
       y = "Number of Fatalities During Shooting Incidents (LOG)") +
  theme_tufte() +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

#injuries during Shooting Incidents (LOG)
gva_injuries_per_yr_log <- ggplot(data = gva_core, aes(x = Year, y = log(Injuries))) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Injuries During Shooting Incidents Over Time (LOG)",
       x = "Year",
       y = "Number of Injuries During Shooting Incidents (LOG)") +
  theme_tufte() +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Average fatalities per Shooting Incidents LOG
gva_fatalities_per_ms_log <- ggplot(data = gva_core, aes(x = Year, y = log(Fatalities/Incidents))) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Average Fatalities per Shooting Incident Over Time (LOG)",
       x = "Year",
       y = "Average Fatalities per Shooting Incident (LOG)") +
  theme_tufte() +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Average injuries per Shooting Incidents LOG
gva_injuries_per_ms_log <- ggplot(data = gva_core, aes(x = Year, y = log(Injuries/Incidents)))+
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Average Injuries per Shooting Incident Over Time (LOG)",
       x = "Year",
       y = "Average Injuries per Shooting Incident (LOG)") +
  theme_tufte() +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))
```

##  
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE, results='asis'}
# GVA
# visualization of ggplots (call gg objects)
# gva movie rates plots
# gva_sing
# gva_multi
# gva_sing_gun
# gva_multi_gun

grid.arrange(gva_sing,gva_multi,gva_sing_gun,gva_multi_gun)
```

##  
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE, results='asis'}
# gva yearly violence counts plots
# gva_incidents_per_yr
# gva_fatalities_per_yr
# gva_injuries_per_yr
# gva_fatalities_per_ms
# gva_injuries_per_ms

grid.arrange(gva_incidents_per_yr,gva_fatalities_per_yr,gva_injuries_per_yr, ncol = 2)
grid.arrange(gva_fatalities_per_ms,gva_injuries_per_ms, ncol = 2)

# gva yearly violence counts LOG plots
# gva_incidents_per_yr_log
# gva_fatalities_per_yr_log
# gva_injuries_per_yr_log
# gva_fatalities_per_ms_log
# gva_injuries_per_ms_log

grid.arrange(gva_incidents_per_yr_log,gva_fatalities_per_yr_log,gva_injuries_per_yr_log, ncol = 2)
grid.arrange(gva_fatalities_per_ms_log,gva_injuries_per_ms_log, ncol = 2)
```
### Section 2   
```{r}

```

### Test First regression for AR and UR  
Base linear model with prime variables of interest:  
*Multiple Acts w/G* (IV) and *Incidents* (DV)  
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# new df for lm
gva_lm <- gva_core
gva_lm.ts <- ts(gva_lm)

# LM Regression
# perform a gva naive regression w/ time trend var
gva_model <- lm(`Incidents` ~ `Multiple Acts w/G` + Year, data = gva_lm)

# print the summary of the model
tab_model(gva_model)

```

### Test for autocorrelation in the errors   
em = residuals from the base linear model   
Lag <= 3  
seems AR not present.  
  
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# check for AR 
# residuals
em <- gva_model$resid
#min(em)
#max(em)
acf(em,xlim =c(0,10), col = "red", lwd =2)
pacf(em,xlim =c(0,10), col = "red", lwd =2)
plot(em)

# durbin-watson test auto* correlation possible AR1
dwt(gva_model, max.lag = 3)
durbinWatsonTest(gva_model, max.lag=3)

# breusch-Godfrey test serial* correlation seems NO AR PRESENT
bgtest(gva_model)
```

### Test for unit roots 
Seems UR is present   
Adding trend (p<0.05)  
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
##### CHECK FOR UNIT ROOTS #### seems like there is UR
# Dickey-Fuller
# augmented Dickey-Fuller test
adfTest(gva_lm.ts[,"Incidents"], lags = 2)
# augmented Dickey-Fuller w/ DRIFT
adfTest(gva_lm.ts[,"Incidents"], lags = 2,type="c")
# augmented Dickey-Fuller w/ TREND
adfTest(gva_lm.ts[,"Incidents"], lags = 1,type="ct")

#  Dickey-Fuller test unit root
summary(ur.df(gva_lm.ts[,"Incidents"], lags = 2, type="trend"))
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# function set
# First differencing function from QMSS package
firstD <- function(var, group, df){
  bad <- (missing(group) & !missing(df))
  if (bad) stop("if df is specified then group must also be specified")

  fD <- function(j){ c(NA, diff(j)) }

  var.is.alone <- missing(group) & missing(df)

  if (var.is.alone) {
    return(fD(var))
    }
  if (missing(df)){
    V <- var
    G <- group }
  else{
    V <- df[, deparse(substitute(var))]
    G <- df[, deparse(substitute(group))]
  }

  G <- list(G)
  D.var <- by(V, G, fD)
  unlist(D.var)
  }
```
### Section 3
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# df set
# get first differences for vars
gva_lm_FD <- gva_lm %>%
  summarise(Year = Year,
            `Single Act FD` = firstD(gva_lm[,"Single Act"]),
            `Multiple Acts FD` = firstD(gva_lm[,"Multiple Acts"]),
            `Single Act w/G FD` = firstD(gva_lm[,"Single Act w/G"]),
            `Multiple Acts w/G FD` = firstD(gva_lm[,"Multiple Acts w/G"]),
            `Incidents FD` = firstD(gva_lm[,"Incidents"]),
            `Fatalities FD` = firstD(gva_lm[,"Fatalities"]),
            `Injuries FD` = firstD(gva_lm[,"Injuries"]),
            `Fatalities/Shootings FD` = firstD(gva_lm[,"Fatalities"]/ gva_lm[,"Incidents"]),
            `Injuries/Shootings FD` = firstD(gva_lm[,"Injuries"]/ gva_lm[,"Incidents"]),
            `GDP in Billions FD` = firstD(gva_lm[,"GDP in Billions"]),
            `FA Weapons Ban FD` = firstD(gva_lm[,"FA Weapons Ban"]),
            `Major US Military Involvement FD` = firstD(gva_lm[,"Major US Military Involvement"]))

# merge by "Year"
gva_lm_Total <- merge(gva_lm,gva_lm_FD, by = "Year")

# convert to ts objects
gva_lm_TFD.ts <- ts(gva_lm_Total)
```



### Multiple Modelings with at least one incident with GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Incidents First Differencing
# LM Regression
# perform a gva  naive regression w/ time trend var
gva_model <- lm(`Incidents FD` ~ `Multiple Acts w/G FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrl1 <- lm(`Incidents FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD`, data = gva_lm_Total)

gva_cntrl2 <- lm(`Incidents FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)
gva_cntrl3 <- lm(`Incidents FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` +
                  `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_model)
summary(gva_cntrl1)
summary(gva_cntrl2)
summary(gva_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_model,gva_cntrl1,gva_cntrl2,gva_cntrl3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Fatalities First Differencing
# LM Regression
# perform a gva naive regression w/ time trend var
gva_modelF <- lm(`Fatalities FD` ~ `Multiple Acts w/G FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlF1 <- lm(`Fatalities FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD`, data = gva_lm_Total)

gva_cntrlF2 <- lm(`Fatalities FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)
gva_cntrlF3 <- lm(`Fatalities FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelF)
summary(gva_cntrlF1)
summary(gva_cntrlF2)
summary(gva_cntrlF3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelF,gva_cntrlF1,gva_cntrlF2,gva_cntrlF3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Injuries First Differencing
# LM Regression
# perform a gva naive regression w/ time trend var
gva_modelI <- lm(`Injuries FD` ~ `Multiple Acts w/G FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlI1 <- lm(`Injuries FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` , data = gva_lm_Total)

gva_cntrlI2 <- lm(`Injuries FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)

gva_cntrlI3 <- lm(`Injuries FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelI)
summary(gva_cntrlI1)
summary(gva_cntrlI2)
summary(gva_cntrlI3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelI,gva_cntrlI1,gva_cntrlI2,gva_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Fatalities/Shootings First Differencing
# LM Regression
# perform a gva naive regression w/ time trend var
gva_modelF <- lm(`Fatalities/Shootings FD` ~ `Multiple Acts w/G FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlF1 <- lm(`Fatalities/Shootings FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD`, data = gva_lm_Total)

gva_cntrlF2 <- lm(`Fatalities/Shootings FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + 
                   `FA Weapons Ban FD`, data = gva_lm_Total)
gva_cntrlF3 <- lm(`Fatalities/Shootings FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + 
                   `FA Weapons Ban FD` + `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelF)
summary(gva_cntrlF1)
summary(gva_cntrlF2)
summary(gva_cntrlF3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelF,gva_cntrlF1,gva_cntrlF2,gva_cntrlF3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Injuries/Shootings First Differncing
# LM Regression
# perform a gva naive regression w/ time trend var
gva_modelI <- lm(`Injuries/Shootings FD` ~ `Multiple Acts w/G FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlI1 <- lm(`Injuries/Shootings FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` , data = gva_lm_Total)

gva_cntrlI2 <- lm(`Injuries/Shootings FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + 
                   `FA Weapons Ban FD`, data = gva_lm_Total)

gva_cntrlI3 <- lm(`Injuries/Shootings FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + 
                   `FA Weapons Ban FD` + `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelI)
summary(gva_cntrlI1)
summary(gva_cntrlI2)
summary(gva_cntrlI3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelI,gva_cntrlI1,gva_cntrlI2,gva_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```

### Multiple Modeling incidents NO GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Incidents First Differencing
# LM Regression
# perform a gva_multi naive regression
gva_model <- lm(`Incidents FD` ~ `Multiple Acts FD` + Year, data = gva_lm_Total)

# perform some gva_multi multiple regressions
gva_cntrl1 <- lm(`Incidents FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` , data = gva_lm_Total)

gva_cntrl2 <- lm(`Incidents FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)
gva_cntrl3 <- lm(`Incidents FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_model)
summary(gva_cntrl1)
summary(gva_cntrl2)
summary(gva_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_model,gva_cntrl1,gva_cntrl2,gva_cntrl3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Fatalities First Differencing
# LM Regression
# perform a gva naive regression w/ time trend bvar
gva_modelF <- lm(`Fatalities FD` ~ `Multiple Acts FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlF1 <- lm(`Fatalities FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD`, data = gva_lm_Total)

gva_cntrlF2 <- lm(`Fatalities FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)
gva_cntrlF3 <- lm(`Fatalities FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelF)
summary(gva_cntrlF1)
summary(gva_cntrlF2)
summary(gva_cntrlF3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelF,gva_cntrlF1,gva_cntrlF2,gva_cntrlF3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Injuries First Differencing
# LM Regression
# perform a gva naive regression
gva_modelI <- lm(`Injuries FD` ~ `Multiple Acts FD` + Year, data = gva_lm_Total)

# perform a gva multiple regression
gva_cntrlI1 <- lm(`Injuries FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` , data = gva_lm_Total)

gva_cntrlI2 <- lm(`Injuries FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)

gva_cntrlI3 <- lm(`Injuries FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelI)
summary(gva_cntrlI1)
summary(gva_cntrlI2)
summary(gva_cntrlI3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelI,gva_cntrlI1,gva_cntrlI2,gva_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Fatalities/Shootings First Differencing
# LM Regression
# perform a gva naive regression w/ time trend var
gva_modelF <- lm(`Fatalities/Shootings FD` ~ `Multiple Acts FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlF1 <- lm(`Fatalities/Shootings FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD`, data = gva_lm_Total)

gva_cntrlF2 <- lm(`Fatalities/Shootings FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)
gva_cntrlF3 <- lm(`Fatalities/Shootings FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelF)
summary(gva_cntrlF1)
summary(gva_cntrlF2)
summary(gva_cntrlF3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelF,gva_cntrlF1,gva_cntrlF2,gva_cntrlF3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA 
# Injuries First Differencing
# LM Regression
# perform a gva naive regression w/ time trend var
gva_modelI <- lm(`Injuries/Shootings FD` ~ `Multiple Acts FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlI1 <- lm(`Injuries/Shootings FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` , data = gva_lm_Total)

gva_cntrlI2 <- lm(`Injuries/Shootings FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)

gva_cntrlI3 <- lm(`Injuries/Shootings FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelI)
summary(gva_cntrlI1)
summary(gva_cntrlI2)
summary(gva_cntrlI3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelI,gva_cntrlI1,gva_cntrlI2,gva_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```


### Single Modeling incident with GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Incidents First Differencing
# LM Regression
# perform a gva_multi naive regression w/ time trend var
gva_model <- lm(`Incidents FD` ~ `Single Act w/G FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrl1 <- lm(`Incidents FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` , data = gva_lm_Total)

gva_cntrl2 <- lm(`Incidents FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)
gva_cntrl3 <- lm(`Incidents FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_model)
summary(gva_cntrl1)
summary(gva_cntrl2)
summary(gva_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_model,gva_cntrl1,gva_cntrl2,gva_cntrl3)
       
tab_model(models,show.ci = FALSE)
```


```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Fatalities First Differnecing
# LM Regression
# perform a gva naive regression w/ time trend var
gva_modelF <- lm(`Fatalities FD` ~ `Single Act w/G FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlF1 <- lm(`Fatalities FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD`, data = gva_lm_Total)

gva_cntrlF2 <- lm(`Fatalities FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)
gva_cntrlF3 <- lm(`Fatalities FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelF)
summary(gva_cntrlF1)
summary(gva_cntrlF2)
summary(gva_cntrlF3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelF,gva_cntrlF1,gva_cntrlF2,gva_cntrlF3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Injuries First Differencing
# LM Regression
# perform a gva naive regression
gva_modelI <- lm(`Injuries FD` ~ `Single Act w/G FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlI1 <- lm(`Injuries FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD`, data = gva_lm_Total)

gva_cntrlI2 <- lm(`Injuries FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)

gva_cntrlI3 <- lm(`Injuries FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelI)
summary(gva_cntrlI1)
summary(gva_cntrlI2)
summary(gva_cntrlI3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelI,gva_cntrlI1,gva_cntrlI2,gva_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA 
# Fatalities/Shootings First Differencing
# LM Regression
# perform a gva naive regression
gva_modelF <- lm(`Fatalities/Shootings FD` ~ `Single Act w/G FD` + Year, data = gva_lm_Total)

# perform a gva multiple regression
gva_cntrlF1 <- lm(`Fatalities/Shootings FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD`, data = gva_lm_Total)

gva_cntrlF2 <- lm(`Fatalities/Shootings FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)
gva_cntrlF3 <- lm(`Fatalities/Shootings FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` +
                   `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelF)
summary(gva_cntrlF1)
summary(gva_cntrlF2)
summary(gva_cntrlF3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelF,gva_cntrlF1,gva_cntrlF2,gva_cntrlF3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA 
# Injuries/Shootings First Differencing
# LM Regression
# perform a gva naive regression w/ time trend var
gva_modelI <- lm(`Injuries/Shootings FD` ~ `Single Act w/G FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlI1 <- lm(`Injuries/Shootings FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` , data = gva_lm_Total)

gva_cntrlI2 <- lm(`Injuries/Shootings FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)

gva_cntrlI3 <- lm(`Injuries/Shootings FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total) 
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelI)
summary(gva_cntrlI1)
summary(gva_cntrlI2)
summary(gva_cntrlI3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelI,gva_cntrlI1,gva_cntrlI2,gva_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```


### Single Modeling incident NO GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Incidents First Differencing
# LM Regression
# perform a gva_multi naive regression w/ time trend var
gva_model <- lm(`Incidents FD` ~ `Single Act FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrl1 <- lm(`Incidents FD` ~ `Single Act FD` + Year + `GDP in Billions FD` , data = gva_lm_Total)

gva_cntrl2 <- lm(`Incidents FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)
gva_cntrl3 <- lm(`Incidents FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_model)
summary(gva_cntrl1)
summary(gva_cntrl2)
summary(gva_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_model,gva_cntrl1,gva_cntrl2,gva_cntrl3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA 
# Fatalities First Differencing
# LM Regression
# perform a gva naive regression w/ time trend var
gva_modelF <- lm(`Fatalities FD` ~ `Single Act FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlF1 <- lm(`Fatalities FD` ~ `Single Act FD` + Year + `GDP in Billions FD`, data = gva_lm_Total)

gva_cntrlF2 <- lm(`Fatalities FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)
gva_cntrlF3 <- lm(`Fatalities FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelF)
summary(gva_cntrlF1)
summary(gva_cntrlF2)
summary(gva_cntrlF3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelF,gva_cntrlF1,gva_cntrlF2,gva_cntrlF3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA 
# Injuries First Differencing
# LM Regression
# perform a gva naive regression w/ time trend var
gva_modelI <- lm(`Injuries FD` ~ `Single Act FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlI1 <- lm(`Injuries FD` ~ `Single Act FD` + Year + `GDP in Billions FD` , data = gva_lm_Total)

gva_cntrlI2 <- lm(`Injuries FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)

gva_cntrlI3 <- lm(`Injuries FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelI)
summary(gva_cntrlI1)
summary(gva_cntrlI2)
summary(gva_cntrlI3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelI,gva_cntrlI1,gva_cntrlI2,gva_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Fatalities/Shootings First Differencing
# LM Regression
# perform a gva naive regression w/ time trend var 
gva_modelF <- lm(`Fatalities/Shootings FD` ~ `Single Act FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlF1 <- lm(`Fatalities/Shootings FD` ~ `Single Act FD` + Year + `GDP in Billions FD`, data = gva_lm_Total)

gva_cntrlF2 <- lm(`Fatalities/Shootings FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)
gva_cntrlF3 <- lm(`Fatalities/Shootings FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelF)
summary(gva_cntrlF1)
summary(gva_cntrlF2)
summary(gva_cntrlF3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
# Model Table
models <- list(gva_modelF,gva_cntrlF1,gva_cntrlF2,gva_cntrlF3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA 
# Injuries/Shootings First Differencing
# LM Regression
# perform a gva naive regression w/ time trend var
gva_modelI <- lm(`Injuries/Shootings FD` ~ `Single Act FD` + Year, data = gva_lm_Total)

# perform some gva multiple regressions
gva_cntrlI1 <- lm(`Injuries/Shootings FD` ~ `Single Act FD` + Year + `GDP in Billions FD` , data = gva_lm_Total)

gva_cntrlI2 <- lm(`Injuries/Shootings FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = gva_lm_Total)

gva_cntrlI3 <- lm(`Injuries/Shootings FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = gva_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(gva_modelI)
summary(gva_cntrlI1)
summary(gva_cntrlI2)
summary(gva_cntrlI3)

```

##   
```{r , include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE, results='asis'}
# GVA
# Model Table
models <- list(gva_modelI,gva_cntrlI1,gva_cntrlI2,gva_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```
