---
title: "Appendix 1a:" 
subtitle: "Small Arms Survey (SAS) Analysis Results"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## load packages
require(readxl)
require(data.table)
require(tidyverse)
require(dplyr)
require(car)
require(lmtest)
require(sandwich)
require(psych)
require(tseries)
require(fUnitRoots)
require(urca)
require(TSA)
require(forecast)
require(ggplot2)
require(ggthemes)
require(corrplot)
require(sjPlot)
require(gridExtra)
```


```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# read in data files
# Small Arms Survey Global Violent Deaths: USA 2004-2020
sas <- read_excel("/Data/SAS_film_0420_rates.xlsx")
```

### Section 1   
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# df set
# vars and correlation
sas_cor <- sas[,c(1,8:11,14:16,18)]

# rename vars
sas_cor <- sas_cor %>%
  rename(`Single Act` = single_rate,
         `Multiple Acts` = multiple_rate,
         `Single Act w/G` = single_rate_gun,
         `Multiple Acts w/G` = multiple_rate_gun,
         `FA Weapons Ban` = `FAWB (tighten)`,
         `Major US Military Involvement` = `Major military involvement`,
         `Violent Deaths per 100K` = `Violent deaths per 100,000 people`)

# aggregate and get means 
sas_cor <- aggregate(subset(sas_cor, sel = -Year), list(year = sas_cor$Year), mean, na.rm=T)
sas_core <- sas_cor %>%
  rename(Year = year)

# make into ts object
sas_cor_ts <- ts(sas_cor)
```

### Descriptive Statistics
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# correlations and visualizations
# descriptives
tab_df(describe(sas_cor_ts),
  title = "Small Arms Survey",
  show.rownames = TRUE)
```

### Correlations
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# create a sas correlation matrix
sas_cor_matrix <- cor(sas_cor_ts, use = "complete.obs")
tab_corr(sas_cor_matrix)
```

### Visualizations
### Correlation Table
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# create a sas correlation plot
corrplot(sas_cor_matrix[c(1:5,9),c(1:5,9)], method = "number",number.cex = 0.9, tl.col = "black", tl.cex = 0.95, tl.offset = 0.2)

```

### Independent and Dependent Variable Time Trends   
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# sas objects for gg plot
# Single Act
sas_single <- sas_core %>%
  group_by(Year,`Single Act`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Multiple Act
sas_multi <- sas_core %>%
  group_by(Year,`Multiple Acts`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Single Act w/Gun
sas_single_gun <- sas_core %>%
  group_by(Year,`Single Act w/G`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Multiple Act w/Gun
sas_multi_gun <- sas_core %>%
  group_by(Year,`Multiple Acts w/G`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()
```


```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# sas movie ggplots
# Single Act
sas_sing <- ggplot(data = sas_single, aes(x = Year, y = `Single Act`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with a Single Modeled Act \nof Violence Over Time",
       subtitle = "Modeled Act w/o Firearm",
       x = "Year",
       y = "Single Modeled Act of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Multiple Act
sas_multi <- ggplot(data = sas_multi, aes(x = Year, y = `Multiple Acts`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with Multiple Modeled Acts \nof Violence Over Time",
       subtitle = "Modeled Acts w/o Firearms",
       x = "Year",
       y = "Multiple Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))


# Single Act w/Gun
sas_sing_gun <- ggplot(data = sas_single_gun, aes(x = Year, y = `Single Act w/G`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with a Single Modeled Act \nof Violence Over Time",
       subtitle = "Modeled Act w/ Firearm",
       x = "Year",
       y = "Single Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))


# Multiple Act w/Gun
sas_multi_gun <- ggplot(data = sas_multi_gun, aes(x = Year, y = `Multiple Acts w/G`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with Multiple Modeled Acts \nof Violence Over Time",
       subtitle = "Modeled Acts w/ At Least One Firearm Instance",
       x = "Year",
       y = "Multiple Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))
```

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# sas violent deaths ggplots
# sas violent deaths per 100K
sas_death_per_yr <- ggplot(data = sas_core, aes(x = Year, y = `Violent Deaths per 100K`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Violent Deaths per 100K per Year",
       x = "Year",
       y = "Number of Violent Deaths per 100K") +
  theme_tufte() +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# sas violent deaths per 100K LOG per year
sas_death_per_yr_log <- ggplot(data = sas_core, aes(x = Year, y = log(`Violent Deaths per 100K`))) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Violent Deaths per 100K per Year (LOG)",
       x = "Year",
       y = "Number of Violent Deaths per 100K (LOG)") +
  theme_tufte() +
  # # Add dotted lines to mark the start and end of weapons ban
  # geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  # geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  # annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))
```

##   
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# visualization of ggplots (call gg objects)
# sas movie rates plots
# sas_sing
# sas_multi
# sas_sing_gun
# sas_multi_gun

grid.arrange(sas_sing,sas_multi,sas_sing_gun,sas_multi_gun)
grid.arrange(sas_death_per_yr,sas_death_per_yr_log, ncol=2)
```

### Section 2
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# sas yearly assault injury counts plots
# sas_death_per_yr

# sas yearly assault injury counts LOG plots
# sas_death_per_yr_log
# grid.arrange(sas_death_per_yr,sas_death_per_yr_log, ncol=2)

```
 
```{r}

```
### Test First regression for AR and UR   
Base linear model with prime variables of interest:   
*Multiple Acts w/G* (IV) and *Violent Deaths per 100K* (DV)  
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# new df for lm
sas_lm <- sas_core
sas_lm.ts <- ts(sas_lm)

# LM Regression
# perform a sas naive regression w/ time trend var
sas_model <- lm(`Violent Deaths per 100K` ~ `Multiple Acts w/G` + Year, data = sas_lm)

# print the summary of the model
tab_model(sas_model)

```

### Tests for autocorrelation in the errors 
em = residuals from the base linear model  
Lag <= 3  
Seems  AR1 is present.   
  
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# check for AR 
# residuals
em <- sas_model$resid
#min(em)
#max(em)
acf(em,xlim =c(0,10), col = "red", lwd =2)
pacf(em,xlim =c(0,10), col = "red", lwd =2)
plot(em)

# durbin-watson test auto* correlation (strongest evidence for AR1)
dwt(sas_model, max.lag = 3)
durbinWatsonTest(sas_model, max.lag=3)

# breusch-Godfrey test serial* correlation AR PRESENT
bgtest(sas_model)
```

### Test for unit roots   
Seems UR is present   
Adding drift or trend (p>0.05)  
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
##### CHECK FOR UNIT ROOTS #### seems like there is UR
# Dickey-Fuller
# augmented Dickey-Fuller test
adfTest(sas_lm.ts[,"Violent Deaths per 100K"], lags = 3)
# augmented Dickey-Fuller w/ DRIFT
adfTest(sas_lm.ts[,"Violent Deaths per 100K"], lags = 3,type="c")
# augmented Dickey-Fuller w/ TREND
adfTest(sas_lm.ts[,"Violent Deaths per 100K"], lags = 3,type="ct")

#  Dickey-Fuller test unit root
summary(ur.df(sas_lm.ts[,"Violent Deaths per 100K"], lags = 3, type="trend"))
```


```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# set function
# First differencing function from QMSS package
firstD <- function(var, group, df){
  bad <- (missing(group) & !missing(df))
  if (bad) stop("if df is specified then group must also be specified")

  fD <- function(j){ c(NA, diff(j)) }

  var.is.alone <- missing(group) & missing(df)

  if (var.is.alone) {
    return(fD(var))
    }
  if (missing(df)){
    V <- var
    G <- group }
  else{
    V <- df[, deparse(substitute(var))]
    G <- df[, deparse(substitute(group))]
  }

  G <- list(G)
  D.var <- by(V, G, fD)
  unlist(D.var)
  }
```

### Section 3
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# set df
# get first differences for vars
sas_lm_FD <- sas_lm %>%
  summarise(Year = Year,
            `Single Act FD` = firstD(sas_lm[,"Single Act"]),
            `Multiple Acts FD` = firstD(sas_lm[,"Multiple Acts"]),
            `Single Act w/G FD` = firstD(sas_lm[,"Single Act w/G"]),
            `Multiple Acts w/G FD` = firstD(sas_lm[,"Multiple Acts w/G"]),
            `Violent Deaths per 100K FD` = firstD(sas_lm[,"Violent Deaths per 100K"]),
            `GDP in Billions FD` = firstD(sas_lm[,"GDP in Billions"]),
            `FA Weapons Ban FD` = firstD(sas_lm[,"FA Weapons Ban"]),
            `Major US Military Involvement FD` = firstD(sas_lm[,"Major US Military Involvement"]))

# merge by "Year"
sas_lm_Total <- merge(sas_lm,sas_lm_FD, by = "Year")

# convert to ts objects
sas_lm_TFD.ts <- ts(sas_lm_Total)
```

### Multiple Modelings with at least one incident with GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS 
# Deaths per 100K First Differences
# LM Regression
# perform a sas naive regression w/ time trend var
sas_model <- lm(`Violent Deaths per 100K FD` ~ `Multiple Acts w/G FD` + Year, data = sas_lm_Total)

# perform some sas multiple regressions
sas_cntrl1 <- lm(`Violent Deaths per 100K FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD`, data = sas_lm_Total)

sas_cntrl2 <- lm(`Violent Deaths per 100K FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = sas_lm_Total)
sas_cntrl3 <- lm(`Violent Deaths per 100K FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + `Major US Military Involvement FD`, data = sas_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(sas_model)
summary(sas_cntrl1)
summary(sas_cntrl2)
summary(sas_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# Model Table
models <- list(sas_model,sas_cntrl1,sas_cntrl2,sas_cntrl3)
       
tab_model(models,show.ci = FALSE)
```


### Multiple Modeling incidents NO GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS 
# Deaths per 100K First Differences
# LM Regression
# perform a sas naive regression w/ time trend var
sas_model4 <- lm(`Violent Deaths per 100K FD` ~ `Multiple Acts FD` + Year, data = sas_lm_Total)

# perform some sas multiple regressions
sas_cntrl5 <- lm(`Violent Deaths per 100K FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD`, data = sas_lm_Total)

sas_cntrl6 <- lm(`Violent Deaths per 100K FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = sas_lm_Total)
sas_cntrl7 <- lm(`Violent Deaths per 100K FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = sas_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(sas_model4)
summary(sas_cntrl5)
summary(sas_cntrl6)
summary(sas_cntrl7)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# Model Table
models <- list(sas_model4,sas_cntrl5,sas_cntrl6,sas_cntrl7)
       
tab_model(models,show.ci = FALSE)
```


### Single Modeling incident with GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS 
# Deaths per 100K First Differences
# LM Regression
# perform a sas naive regression w/ time trend var
sas_model8 <- lm(`Violent Deaths per 100K FD` ~ `Single Act w/G FD` + Year, data = sas_lm_Total)

# perform some sas multiple regressions
sas_cntrl9 <- lm(`Violent Deaths per 100K FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD`, data = sas_lm_Total)

sas_cntrl10 <- lm(`Violent Deaths per 100K FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = sas_lm_Total)
sas_cntrl11 <- lm(`Violent Deaths per 100K FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = sas_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(sas_model8)
summary(sas_cntrl9)
summary(sas_cntrl10)
summary(sas_cntrl11)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# Model Table
models <- list(sas_model8,sas_cntrl9,sas_cntrl10,sas_cntrl11)
       
tab_model(models,show.ci = FALSE)
```


### Single Modeling incident NO GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS 
# Deaths per 100K First Differences
# LM Regression
# perform a sas naive regression w/ time trend var
sas_model12 <- lm(`Violent Deaths per 100K FD` ~ `Single Act FD` + Year, data = sas_lm_Total)

# perform some sas multiple regressions
sas_cntrl13 <- lm(`Violent Deaths per 100K FD` ~ `Single Act FD` + Year + `GDP in Billions FD`, data = sas_lm_Total)

sas_cntrl14 <- lm(`Violent Deaths per 100K FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = sas_lm_Total)
sas_cntrl15 <- lm(`Violent Deaths per 100K FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = sas_lm_Total)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(sas_model12)
summary(sas_cntrl13)
summary(sas_cntrl14)
summary(sas_cntrl15)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# SAS
# Model Table
models <- list(sas_model12,sas_cntrl13,sas_cntrl14,sas_cntrl15)
       
tab_model(models,show.ci = FALSE)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# # SAS
# # Model Table
# models <- list(sas_model,sas_cntrl1,sas_cntrl2,sas_cntrl3,
#                sas_model4,sas_cntrl5,sas_cntrl6,sas_cntrl7,
#                sas_model8,sas_cntrl9,sas_cntrl10,sas_cntrl11,
#                sas_model12,sas_cntrl13,sas_cntrl14,sas_cntrl15)
#        
# tab_model(models,show.ci = FALSE)
```