---
title: "Appendix 2c:" 
subtitle: "Uniform Crime Reports (UCR) Analysis Results"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## load packages
require(readxl)
require(writexl)
require(data.table)
require(tidyverse)
require(dplyr)
require(car)
require(lmtest)
require(sandwich)
require(psych)
require(tseries)
require(fUnitRoots)
require(urca)
require(TSA)
require(forecast)
require(ggplot2)
require(ggthemes)
require(corrplot)
require(sjPlot)
require(gridExtra)
```


```{r , include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# read in .tsv data files
# Uniform Crime Reports Supplementary Homicide Reports 1976-2007
ucr <- data.table(read.table("/Data/film_data/Data/UCR_film_7607_rates.tsv",header=TRUE, sep="\t"))
```

### Section 1   
```{r , include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# df set
# vars and correlation
ucr_cor <- ucr[,c(1,8:11,14:16, 18,19)]

# rename vars
ucr_cor <- ucr_cor %>%
  rename(`Single Act` = single_rate,
         `Multiple Acts` = multiple_rate,
         `Single Act w/G` = single_rate_gun,
         `Multiple Acts w/G` = multiple_rate_gun,
         `GDP in Billions` = GDP.in.Billions,
         `FA Weapons Ban` = FAWB..tighten.,
         `Major US Military Involvement` = Major.military.involvement,
         Incident = incidents_per_yr,
         `Gun Incident` = gun_incidents_per_yr)

# aggregate and get means 
ucr_cor <- aggregate(subset(ucr_cor, sel = -Year), list(year = ucr_cor$Year), mean, na.rm=T) 
ucr_cor <- ucr_cor %>%
  rename(Year = year) %>%
   mutate(`Gun Homicides/Homicides` = `Gun Incident`/Incident)

# df for later
ucr_core <- ucr_cor 

# make into ts object
ucr_cor_ts <- ts(ucr_cor)
```

### Descriptive Statistics
```{r , echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# correlations and visualizations
# descriptives
tab_df(describe(ucr_cor_ts),
  title = "Uniform Crime Reports",
  show.rownames = TRUE)
```

### Correlations
```{r , echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# create a ucr correlation matrix
ucr_cor_matrix <- cor(ucr_cor_ts, use = "complete.obs")
tab_corr(ucr_cor_matrix)
```

### Visualizations
### Correlation Table
```{r , echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# create a ucr correlation plot
corrplot(ucr_cor_matrix[c(1:5,9:11),c(1:5,9:11)], method = "number",number.cex = 0.8, tl.col = "black", tl.cex = 0.95, tl.offset = 0.2)
```

### Independent and Dependent Variable Time Trends 
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# objects for gg plot
# Single Act
ucr_single <- ucr_core %>%
  group_by(Year,`Single Act`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Multiple Act
ucr_multi <- ucr_core %>%
  group_by(Year,`Multiple Acts`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Single Act w/Gun
ucr_single_gun <- ucr_core %>%
  group_by(Year,`Single Act w/G`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()

# Multiple Act w/Gun
ucr_multi_gun <- ucr_core %>%
  group_by(Year,`Multiple Acts w/G`) %>%
  distinct(.keep_all = FALSE) %>%
  summarise()
```


```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR 
# movie ggplots
# Single Act
ucr_sing <- ggplot(data = ucr_single, aes(x = Year, y = `Single Act`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with a Single Modeled Act \nof Violence Over Time",
       subtitle = "Modeled Act w/o Firearm",
       x = "Year",
       y = "Single Modeled Act of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Multiple Act
ucr_multi <- ggplot(data = ucr_multi, aes(x = Year, y = `Multiple Acts`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with Multiple Modeled Acts \nof Violence Over Time",
       subtitle = "Modeled Acts w/o Firearms",
       x = "Year",
       y = "Multiple Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Single Act w/Gun
ucr_sing_gun <- ggplot(data = ucr_single_gun, aes(x = Year, y = `Single Act w/G`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with a Single Modeled Act \nof Violence Over Time",
       subtitle = "Modeled Act w/ Firearm",
       x = "Year",
       y = "Single Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# Multiple Act w/Gun
ucr_multi_gun <- ggplot(data = ucr_multi_gun, aes(x = Year, y = `Multiple Acts w/G`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Top Ten Movies with Multiple Modeled Acts \nof Violence Over Time",
       subtitle = "Modeled Acts w/ At Least One Firearm Instance",
       x = "Year",
       y = "Multiple Modeled Acts of Violence (Rates)") +
  theme_tufte() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR 
# Homicide ggplots
# homicide incidents
ucr_incidents_per_yr <- ggplot(data = ucr_core, aes(x = Year, y = Incident)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Homicides Over Time",
       x = "Year",
       y = "Number of Homicides") +
  theme_tufte() +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# gun homicide incident
ucr_gun_inc_per_yr <- ggplot(data = ucr_core, aes(x = Year, y = `Gun Incident`)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Gun Homicides Over Time",
       x = "Year",
       y = "Number of Gun Homicides") +
  theme_tufte() +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# rate of gun homicides to homicides 
ucr_gun_homicide <- ggplot(data = ucr_core, aes(x = Year, y = `Gun Incident`/Incident)) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Gun-Homicide to Homicide Over Time",
       x = "Year",
       y = "Rates of Gun-Homicide to Homicide") +
  theme_tufte() +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))


```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR 
# Homicide ggplots
# homicide incidents (LOG)
ucr_incidents_per_yr_log <- ggplot(data = ucr_core, aes(x = Year, y = log(Incident))) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Homicides Over Time (LOG)",
       x = "Year",
       y = "Number of Homicides (LOG)") +
  theme_tufte() +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# gun homicide incident
ucr_gun_inc_per_yr_log <- ggplot(data = ucr_core, aes(x = Year, y = log(`Gun Incident`))) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Gun Homicides Over Time (LOG)",
       x = "Year",
       y = "Number of Gun Homicides (LOG)") +
  theme_tufte() +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))

# rate of gun homicides to homicides 
ucr_gun_homicide_log <- ggplot(data = ucr_core, aes(x = Year, y = log(`Gun Incident`/Incident))) +
  geom_line(color = "black", size = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
  labs(title = "Rates of Gun-Homicide to Homicide Over Time (LOG)",
       x = "Year",
       y = "Rates of Gun-Homicide to Homicide (LOG)") +
  theme_tufte() +
  # Add dotted lines to mark the start and end of weapons ban
  geom_vline(xintercept = 1994, linetype = "dotted", color = "grey", size = 0.7) +
  geom_vline(xintercept = 2004, linetype = "dotted", color = "grey", size = 0.7) +
  annotate("text", x = 1999, y = 0.07,color = "black", label = "Firearm Weapons Ban", size = 1.8) +
  theme(text = element_text(size = 8),
  axis.text = element_text(size = 7),
  axis.title = element_text(size = 7),
  legend.title = element_text(size = 8))
```

##   
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# visualization of ggplots (call gg objects)
# movie rates plots
# ucr_sing
# ucr_multi
# ucr_sing_gun
# ucr_multi_gun

grid.arrange(ucr_sing,ucr_multi,ucr_sing_gun,ucr_multi_gun)
```

##   
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# homicides
# ucr_incidents_per_yr
# ucr_gun_inc_per_yr
# ucr_gun_homicide

grid.arrange(ucr_incidents_per_yr,ucr_gun_inc_per_yr,ucr_gun_homicide, ncol = 2)

# homicides log
# ucr_incidents_per_yr_log
# ucr_gun_inc_per_yr_log
# ucr_gun_homicide_log
grid.arrange(ucr_incidents_per_yr_log,ucr_gun_inc_per_yr_log,ucr_gun_homicide_log, ncol = 2)
```

### Section 2   
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
```

### Test First regression for AR and UR   
Base linear model with prime variables of interest:  
*Multiple Acts w/G* (IV) and *Incident* (DV)   
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# new df for lm
ucr_lm <- ucr_core
ucr_lm.ts <- ts(ucr_lm)

# LM Regression
# perform a ucr naive regression w/ time trend var 
ucr_model <- lm(`Incident` ~ `Multiple Acts w/G` + Year, data = ucr_lm)

# print the summary of the model
tab_model(ucr_model)

```

### Test for autocorrelation in the errors  
em = residuals from the base linear model   
Lag <= 2  
Seems  AR2 is present  

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# check for AR 
# residuals
em <- ucr_model$resid
#min(em)
#max(em)
acf(em,xlim =c(0,10), col = "red", lwd =2) #possible AR2
pacf(em,xlim =c(0,10), col = "red", lwd =2) #partial AR1
plot(em)

# durbin-watson test auto* correlation possible AR2
dwt(ucr_model, max.lag = 3)
durbinWatsonTest(ucr_model, max.lag=3)

# breusch-Godfrey test serial* correlation seems AR PRESENT
bgtest(ucr_model, order = 3)
```

### Test for unit roots  
Seems UR is not present  
Without adding drift or trend (p<0.05)   
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# GVA
##### CHECK FOR UNIT ROOTS #### seems like there is UR
# Dickey-Fuller
# augmented Dickey-Fuller test
adfTest(ucr_lm.ts[,"Incident"], lags = 1)
# augmented Dickey-Fuller w/ DRIFT
adfTest(ucr_lm.ts[,"Incident"], lags = 1,type="c")
# augmented Dickey-Fuller w/ TREND
adfTest(ucr_lm.ts[,"Incident"], lags = 1,type="ct")

#  Dickey-Fuller test unit root
summary(ur.df(ucr_lm.ts[,"Incident"], lags = 1, type="trend"))
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# function set
# First differencing function from QMSS package
firstD <- function(var, group, df){
  bad <- (missing(group) & !missing(df))
  if (bad) stop("if df is specified then group must also be specified")

  fD <- function(j){ c(NA, diff(j)) }

  var.is.alone <- missing(group) & missing(df)

  if (var.is.alone) {
    return(fD(var))
    }
  if (missing(df)){
    V <- var
    G <- group }
  else{
    V <- df[, deparse(substitute(var))]
    G <- df[, deparse(substitute(group))]
  }

  G <- list(G)
  D.var <- by(V, G, fD)
  unlist(D.var)
  }
```
### Section 3
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# df set
# get first differences for vars
ucr_lm_FD <- ucr_lm %>%
  summarise(Year = Year,
            `Year FD` = firstD(ucr_lm[,"Year"]),
            `Single Act FD` = firstD(ucr_lm[,"Single Act"]),
            `Multiple Acts FD` = firstD(ucr_lm[,"Multiple Acts"]),
            `Single Act w/G FD` = firstD(ucr_lm[,"Single Act w/G"]),
            `Multiple Acts w/G FD` = firstD(ucr_lm[,"Multiple Acts w/G"]),
            `Incident FD` = firstD(ucr_lm[,"Incident"]),
            `Gun Incident FD` = firstD(ucr_lm[,"Gun Incident"]),
            `Gun Incident/Incident FD` = firstD(ucr_lm[,"Gun Incident"]/ ucr_lm[,"Incident"]),
            `GDP in Billions FD` = firstD(ucr_lm[,"GDP in Billions"]),
            `FA Weapons Ban FD` = firstD(ucr_lm[,"FA Weapons Ban"]),
            `Major US Military Involvement FD` = firstD(ucr_lm[,"Major US Military Involvement"]))

# merge by "Year"
ucr_lm_Total <- merge(ucr_lm,ucr_lm_FD, by = "Year")

# convert to ts object
ucr_lm_TFD.ts <- ts(ucr_lm_Total)
```


### Multiple Modelings with at least one incident with GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# homicides First Difference
# LM Regression 
# perform a ucr naive regression w/ time trend var
ucr_model <- lm(`Incident FD` ~ `Multiple Acts w/G FD` + Year, data = ucr_lm_TFD.ts)

# perform some ucr multiple regressions
ucr_cntrl1 <- lm(`Incident FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD`, data = ucr_lm_TFD.ts)

ucr_cntrl2 <- lm(`Incident FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = ucr_lm_TFD.ts)
ucr_cntrl3 <- lm(`Incident FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` +
                  `Major US Military Involvement FD`, data = ucr_lm_TFD.ts)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(ucr_model)
summary(ucr_cntrl1)
summary(ucr_cntrl2)
summary(ucr_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Model Table
models <- list(ucr_model,ucr_cntrl1,ucr_cntrl2,ucr_cntrl3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR 
# Gun Incident First Difference
# LM Regression 
# perform a ucr naive regression w/ time trend var
ucr_modelF <- lm(`Gun Incident FD` ~ `Multiple Acts w/G FD` + Year, data = ucr_lm_TFD.ts)

# perform some ucr multiple regressions
ucr_cntrlF1 <- lm(`Gun Incident FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD`, data = ucr_lm_TFD.ts)

ucr_cntrlF2 <- lm(`Gun Incident FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = ucr_lm_TFD.ts)
ucr_cntrlF3 <- lm(`Gun Incident FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = ucr_lm_TFD.ts)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(ucr_modelF)
summary(ucr_cntrlF1)
summary(ucr_cntrlF2)
summary(ucr_cntrlF3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Model Table
models <- list(ucr_modelF,ucr_cntrlF1,ucr_cntrlF2,ucr_cntrlF3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR 
# Gun Incident/Incident First Differences
# LM Regression 
# perform a ucr naive regression w/ time trend var
ucr_modelI <- lm(`Gun Incident/Incident FD` ~ `Multiple Acts w/G FD` + Year, data = ucr_lm_TFD.ts)

# perform some ucr multiple regressions
ucr_cntrlI1 <- lm(`Gun Incident/Incident FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` , data = ucr_lm_TFD.ts)

ucr_cntrlI2 <- lm(`Gun Incident/Incident FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = ucr_lm_TFD.ts)

ucr_cntrlI3 <- lm(`Gun Incident/Incident FD` ~ `Multiple Acts w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = ucr_lm_TFD.ts)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(ucr_modelI)
summary(ucr_cntrlI1)
summary(ucr_cntrlI2)
summary(ucr_cntrlI3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Model Table
models <- list(ucr_modelI,ucr_cntrlI1,ucr_cntrlI2,ucr_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```


### Multiple Modeling incidents NO GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Incident First Differencing
# LM Regression
# perform a ucr naive regression w/ time trend var
ucr_model <- lm(`Incident FD` ~ `Multiple Acts FD` + Year, data = ucr_lm_TFD.ts)

# perform some ucr multiple regressions
ucr_cntrl1 <- lm(`Incident FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` , data = ucr_lm_TFD.ts)

ucr_cntrl2 <- lm(`Incident FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = ucr_lm_TFD.ts)
ucr_cntrl3 <- lm(`Incident FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = ucr_lm_TFD.ts)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(ucr_model)
summary(ucr_cntrl1)
summary(ucr_cntrl2)
summary(ucr_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Model Table
models <- list(ucr_model,ucr_cntrl1,ucr_cntrl2,ucr_cntrl3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR 
# Gun Incident first Differencing
# LM Regression
# perform a ucr naive regression w/ time trend var
ucr_modelF <- lm(`Gun Incident FD` ~ `Multiple Acts FD` + Year, data = ucr_lm_TFD.ts)

# perform some ucr multiple regressions
ucr_cntrlF1 <- lm(`Gun Incident FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD`, data = ucr_lm_TFD.ts)

ucr_cntrlF2 <- lm(`Gun Incident FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = ucr_lm_TFD.ts)
ucr_cntrlF3 <- lm(`Gun Incident FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = ucr_lm_TFD.ts)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(ucr_modelF)
summary(ucr_cntrlF1)
summary(ucr_cntrlF2)
summary(ucr_cntrlF3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Model Table
models <- list(ucr_modelF,ucr_cntrlF1,ucr_cntrlF2,ucr_cntrlF3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR 
# Gun Incident/Incident First Differenceing
# LM Regression
# perform a ucr naive regression w/ time trend var
ucr_modelI <- lm(`Gun Incident/Incident FD` ~ `Multiple Acts FD` + Year, data = ucr_lm_TFD.ts)

# perform some ucr multiple regressions
ucr_cntrlI1 <- lm(`Gun Incident/Incident FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` , data = ucr_lm_TFD.ts)

ucr_cntrlI2 <- lm(`Gun Incident/Incident FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = ucr_lm_TFD.ts)

ucr_cntrlI3 <- lm(`Gun Incident/Incident FD` ~ `Multiple Acts FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = ucr_lm_TFD.ts)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(ucr_modelI)
summary(ucr_cntrlI1)
summary(ucr_cntrlI2)
summary(ucr_cntrlI3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Model Table
models <- list(ucr_modelI,ucr_cntrlI1,ucr_cntrlI2,ucr_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```


### Single Modeling incident with GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Incident First Differencing
# LM Regression
# perform a ucr naive regression w/ time trend var
ucr_model <- lm(`Incident FD` ~ `Single Act w/G FD` + Year, data = ucr_lm_TFD.ts)

# perform some ucr multiple regressions
ucr_cntrl1 <- lm(`Incident FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` , data = ucr_lm_TFD.ts)

ucr_cntrl2 <- lm(`Incident FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = ucr_lm_TFD.ts)
ucr_cntrl3 <- lm(`Incident FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = ucr_lm_TFD.ts)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(ucr_model)
summary(ucr_cntrl1)
summary(ucr_cntrl2)
summary(ucr_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Model Table
models <- list(ucr_model,ucr_cntrl1,ucr_cntrl2,ucr_cntrl3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Gun Incident First Differencing
# LM Regression
# perform a ucr naive regression w/ time trend var
ucr_modelF <- lm(`Gun Incident FD` ~ `Single Act w/G FD` + Year, data = ucr_lm_TFD.ts)

# perform some ucr multiple regressions
ucr_cntrlF1 <- lm(`Gun Incident FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD`, data = ucr_lm_TFD.ts)

ucr_cntrlF2 <- lm(`Gun Incident FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = ucr_lm_TFD.ts)
ucr_cntrlF3 <- lm(`Gun Incident FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = ucr_lm_TFD.ts)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(ucr_modelF)
summary(ucr_cntrlF1)
summary(ucr_cntrlF2)
summary(ucr_cntrlF3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Model Table
models <- list(ucr_modelF,ucr_cntrlF1,ucr_cntrlF2,ucr_cntrlF3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Gun Incident/Incident First Differencing
# LM Regression
# perform a ucr naive regression w/ time trend var
ucr_modelI <- lm(`Gun Incident/Incident FD` ~ `Single Act w/G FD` + Year, data = ucr_lm_TFD.ts)

# perform some ucr multiple regressions
ucr_cntrlI1 <- lm(`Gun Incident/Incident FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD`, data = ucr_lm_TFD.ts)

ucr_cntrlI2 <- lm(`Gun Incident/Incident FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = ucr_lm_TFD.ts)

ucr_cntrlI3 <- lm(`Gun Incident/Incident FD` ~ `Single Act w/G FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = ucr_lm_TFD.ts)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(ucr_modelI)
summary(ucr_cntrlI1)
summary(ucr_cntrlI2)
summary(ucr_cntrlI3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Model Table
models <- list(ucr_modelI,ucr_cntrlI1,ucr_cntrlI2,ucr_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```


### Single Modeling incident NO GUN
```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Incident First Differencing
# LM Regression
# perform a ucr naive regression w/ time trend
ucr_model <- lm(`Incident FD` ~ `Single Act FD` + Year, data = ucr_lm_TFD.ts)

# perform some ucr multiple regressions
ucr_cntrl1 <- lm(`Incident FD` ~ `Single Act FD` + Year + `GDP in Billions FD` , data = ucr_lm_TFD.ts)

ucr_cntrl2 <- lm(`Incident FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = ucr_lm_TFD.ts)
ucr_cntrl3 <- lm(`Incident FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = ucr_lm_TFD.ts)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(ucr_model)
summary(ucr_cntrl1)
summary(ucr_cntrl2)
summary(ucr_cntrl3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Model Table
models <- list(ucr_model,ucr_cntrl1,ucr_cntrl2,ucr_cntrl3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR 
# Gun Incident First Differencing 
# LM Regression
# perform a ucr naive regression w/ time trend var
ucr_modelF <- lm(`Gun Incident FD` ~ `Single Act FD` + Year, data = ucr_lm_TFD.ts)

# perform some ucr multiple regressions
ucr_cntrlF1 <- lm(`Gun Incident FD` ~ `Single Act FD` + Year + `GDP in Billions FD`, data = ucr_lm_TFD.ts)

ucr_cntrlF2 <- lm(`Gun Incident FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = ucr_lm_TFD.ts)
ucr_cntrlF3 <- lm(`Gun Incident FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = ucr_lm_TFD.ts)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(ucr_modelF)
summary(ucr_cntrlF1)
summary(ucr_cntrlF2)
summary(ucr_cntrlF3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Model Table
models <- list(ucr_modelF,ucr_cntrlF1,ucr_cntrlF2,ucr_cntrlF3)
       
tab_model(models,show.ci = FALSE)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR 
# Gun Incident/Incident first Differencing 
# LM Regression
# perform a ucr naive regression w/time trend var
ucr_modelI <- lm(`Gun Incident/Incident FD` ~ `Single Act FD` + Year, data = ucr_lm_TFD.ts)

# perform some ucr multiple regressions
ucr_cntrlI1 <- lm(`Gun Incident/Incident FD` ~ `Single Act FD` + Year + `GDP in Billions FD` , data = ucr_lm_TFD.ts)

ucr_cntrlI2 <- lm(`Gun Incident/Incident FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD`, 
                  data = ucr_lm_TFD.ts)

ucr_cntrlI3 <- lm(`Gun Incident/Incident FD` ~ `Single Act FD` + Year + `GDP in Billions FD` + `FA Weapons Ban FD` + 
                    `Major US Military Involvement FD`, data = ucr_lm_TFD.ts)
```

```{r, include = FALSE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# print the summary of the models
summary(ucr_modelI)
summary(ucr_cntrlI1)
summary(ucr_cntrlI2)
summary(ucr_cntrlI3)
```

##   
```{r, include = TRUE, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# UCR
# Model Table
models <- list(ucr_modelI,ucr_cntrlI1,ucr_cntrlI2,ucr_cntrlI3)
       
tab_model(models,show.ci = FALSE)
```
