---
title: 'Winter Olympics Visualization'
author: "Adrian Varallyay"
always_allow_html: yes
output:
  html_document:
    keep_md: yes
  pdf_document: default
font-family: Helvetica
autosize: yes
---


```{r setup, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#knitr::opts_chunk$set(echo  =  TRUE,warning  =  FALSE, message  =  FALSE) 

#### Loading Libraries
library(ggplot2)    
library(magrittr)
library(dplyr)
library(ggthemes)
library(ggpubr)
library(tidyverse)
library(plotly)
library(DT)
library(ggalt)   
library(ggrepel)
library(rvest)
library(stringr)
library(plotly)
```


```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
# read in files
athletes <- read.csv("data/athletes_and_events.csv")
gdp_pop <- read.csv("data/gdp_pop.csv")
noc_regions <- read.csv("data/noc_regions.csv")
```

## Question 1
#### Manipulating and Joining Data

I combined German designations under German and Russian designations under Russia. All other countries which have changed names over time, were left as is. 
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
# German designations under GER and Russian designations under RUS
athletes$NOC[athletes$NOC %in% c("SAA","EUA","GDR","FRG")] <- "GER"
athletes$NOC[athletes$NOC %in% c("RUS","RU1","URS","EUN",'ROC')] <- "RUS"

# relabel code column
colnames(gdp_pop)[colnames(gdp_pop)  ==  'Code'] <- 'NOC'

# join dfs filter for winter sports
all_data <- athletes %>%
  left_join(noc_regions, by  =  'NOC') %>%
  left_join(gdp_pop,by = 'NOC') %>%
  filter(Season == "Winter")


```

#### Calculate the number of Olympics each country participated in.
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
all_data %>%
    group_by(region) %>%
    summarise(Year_Count  =  n_distinct(Year)) %>%
    arrange(desc(Year_Count)) %>%
    head(20)
```

### Calculate how many medals each country won over time
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
# top 10 country list
top10 <- all_data %>%
    group_by(Country) %>%
    summarise(count  =  n_distinct(Sport,Event,Sex,Medal)) %>%
    arrange(desc(count)) %>% 
    select(Country) %>%
    head(10)

# use country list to filter countries that won medals
top10_byyear <- all_data %>%
    filter(Medal %in% c("Bronze","Silver","Gold"),
           Country %in% top10$Country) %>%
    group_by(Country,Year) %>%
    summarise(Medal_Count  =  n_distinct(Games, Year, Season, Medal, Event, Country)) %>%
    arrange(desc(Medal_Count)) 

# top ten medal winning countries over ~22 years
top10_byyear 
```

### Graph medals overtime by Country - Top 10 Countries

Initially I made a line graph with the top 10 countries and a second where they are separated in facets. I prefer the faceted version because the initial line graph could be much clearer, and the facets make interpretation a little easier.
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
# all countries on one plot
plot1 <- ggplot(top10_byyear, aes(Year,Medal_Count))  + 
  geom_point(aes(color  =  Country))  + 
  geom_line(aes(color  =  Country))  + 
  scale_color_brewer(palette  =  "Set2") + 
  labs(x  =  "Year", y = "Number of Medals", title = "Number of Medals Won by Country per Year")  +  
  theme(legend.position = "bottom")  +  
  theme(plot.title = element_text(hjust  =  0.5))

# facet separated
plot2 <- ggplot(top10_byyear,aes(Year,Medal_Count)) + 
  #theme_tufte(base_size  =  10) + 
  geom_point(aes(), color  =  "#00BFFF") + 
  geom_smooth(aes(), color  =  "#00BFFF",size  =  .5) + 
  facet_grid(rows  =  vars(Country)) + 
  facet_wrap(~Country, ncol = 3) + 
  labs(x = "Year", y = "Number of Medals", title = "Number of Medals Won by Country per Year") +
  theme(plot.title = element_text(hjust  =  0.5))

plot1
plot2
```

#### Calculating the All-time medal totals by Country
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
# top 10 country list
top10 <- all_data %>%
    filter(Medal %in% c("Bronze","Silver","Gold")) %>%
    group_by(Country) %>%
    summarise(count  =  n_distinct(Sport,Event,Sex,Medal,Year)) %>%
    arrange(desc(count)) %>% 
    select(Country) %>%
    head(10)

# use country list to filter countriesand get total medals won
totals_all_time <- all_data %>%
    filter(Medal %in% c("Bronze","Silver","Gold"),
           Country %in% top10$Country) %>% 
    group_by(Country,Medal) %>%
    summarise(Medal_Count  =  n_distinct(Games, Year, Season, Medal, Event, Country)) %>%
    arrange(desc(Medal_Count)) 
```

#### Graph the all-time medal counts by Country
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
# Cumulative Medals Won by top 10 medal winning Countries
plot3 <- ggplot(totals_all_time, aes(x = reorder(Country, desc(Medal_Count), sum), y = Medal_Count, fill = factor(Medal, levels = c("Gold", "Silver", "Bronze"))))  +
  theme_tufte(base_size  =  10)  + 
  labs(fill  =  "Medal")  + 
  labs(x = "Country", y = "Number of Medals", title = "Cumulative Medals Won by Country")  + 
geom_bar(stat = "identity")  + 
  scale_fill_manual(values = c('#F1C935','#C0C0C0','#CD7F32')) + # #EAB31B, #F1C935, or #D6AF36 for gold?
  theme(plot.title = element_text(hjust  =  0.5))

plot3
```

## Question 2  
### Looking only at the Gold medals.  

The graph shows the top 10 countries with the largest difference between any ranks. Some of the big winners (US, Russia, and China) all fall in the rankings when they are adjusted for population. This visualization is a little convoluted. 
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
# cumulative won medals
totals_all_time <- all_data %>%
    filter(Medal %in% c("Gold"), !is.na(GDP.per.Capita)) %>% 
    group_by(Country, Medal, GDP.per.Capita, Population) %>%
    summarise(Medal_Count  =  n_distinct(Games, Year, Season, Medal, Event, Country),
              GDP_per_Gold  =  max(GDP.per.Capita)/n_distinct(Games, Year, Season, Medal, Event, Country),
              Population_per_Gold  =  max(Population)/n_distinct(Games, Year, Season, Medal, Event, Country)) %>%
    arrange((Population_per_Gold)) 

# address rank ties in output
totals_all_time$normal_rank <- rank(desc(totals_all_time$Medal_Count),ties.method  =  "min")
totals_all_time$GDP_rank <- rank(totals_all_time$GDP_per_Gold,ties.method  =  "min")
totals_all_time$Pop_rank <- rank(totals_all_time$Population_per_Gold,ties.method  =  "min")

# reshape df
pivoted <- totals_all_time %>%
 gather(normal_rank:Pop_rank, key  =  "ranking", value  =  "Rank") %>%
  arrange(Country)

# order to ranking
pivoted$order <- case_when(pivoted$ranking  == "normal_rank" ~ 1,
                           pivoted$ranking  ==  "GDP_rank" ~ 2,
                           pivoted$ranking  ==  "Pop_rank" ~ 3)

# get min max rank range for countries
Top10Diff <- pivoted %>%
    group_by(Country) %>% 
    summarise(range  =  max(Rank, na.rm = TRUE) - min(Rank, na.rm = TRUE)) %>%
    arrange(desc(range)) %>%
    head(10)

# filter for top 10 countries
pivoted_top10 <- pivoted %>% 
  filter(Country %in% Top10Diff$Country) 


plot4 <- pivoted %>% 
  filter(Country %in% Top10Diff$Country) %>%
  ggplot(aes(x  =  reorder(ranking,order), y  =  Rank, group  =  Country))  + 
  theme_minimal() + 
  geom_line(aes(color  =  Country), size  =  1)  + 
  scale_color_manual(values = c('#FF3366','#00BFFF','#00BFFF','#9966CC','#9966CC','#FF3366','#00BFFF','#9966CC','#9966CC','#FF3366'))  + 
  geom_point(aes(color  =  Country), size  =  2)  + 
  scale_y_reverse(breaks  =  1:nrow(pivoted))  +
  #theme(legend.position  =  'none')  + 
  geom_text(data  =  pivoted_top10 %>% filter(ranking  ==  "Pop_rank"), 
            aes(label  =  Country, x  =  3.2), fontface  =  "bold", color  =  "Black", size  =  2.5)  +
  labs(x  =  'Ranking Type', y  =  'Rank', title  =  "Top 10 Countries Gold Medal Rankings", 
       subtitle  =  'Gold Medal Ranking for Normal, and  GDP and Population Adjusted')

plot4
```


The graph shows that Russia, United States, China, Italy, etc (the Countries in Blue) ranked better after adjusting for GDP. The countries in purple ranked worse after adjusting for GDP.

```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}

totals_all_time$"GDP_Better" <- case_when(totals_all_time$normal_rank < totals_all_time$GDP_rank ~ "GDP Rank Worse than Normal",
                           totals_all_time$normal_rank > totals_all_time$GDP_rank ~ "GDP Rank Better than Normal",
                           TRUE ~ "Identical Ranks")
totals_all_time$'Pop_Better' <- case_when(totals_all_time$normal_rank< totals_all_time$Pop_rank ~ "Pop Rank Worse than Normal",
                           totals_all_time$normal_rank> totals_all_time$Pop_rank ~ "Pop Rank Better than Normal",
                           TRUE ~ "Identical Ranks")


plot5 <- ggplot(totals_all_time, aes(x = totals_all_time$GDP_rank, y = totals_all_time$normal_rank)) + 
    theme_minimal() + 
    geom_point(aes(color = totals_all_time$GDP_Better)) + 
    scale_color_manual(values = c("#00BFFF","#9966CC",'#FF3366')) + 
    labs(x = "Gold Medal Rank - GDP Adjusted", y = "Normal Gold Medal Rank", title = "GDP Adjusted Rank by Normal Rank", color = 'Rank Type') + 
    theme(legend.position = "bottom") + 
    theme(plot.title = element_text(hjust  =  0.5)) + 
    geom_text_repel(aes(label  =  Country),
              color  =  "gray20", size  =  1.9) + 
    scale_x_continuous(limits = c(0,35)) + 
    scale_y_continuous(limits = c(0,35)) + 
    geom_abline(linetype  =  "dashed") + 
    annotate("text", x = 3, y = 33,label  =  c("Better Ranking \nAdjusted for GDP"), size  =  4, color  =  "#00BFFF") + 
    annotate("text", x = 33, y = 3,label  =  c("Worse Ranking \nAdjusted for GDP"), size  =  4, color  =  "#9966CC")

plot5
```


The graph shows that Olympic winners like Russia, United States, Germany, China, Canada, etc (all Countries in purple) performed much worse after adjusting for population. The countries in blue performed better after adjusting for Population.
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
plot6 <- ggplot(totals_all_time, aes(x = totals_all_time$Pop_rank, y = totals_all_time$normal_rank)) + 
    theme_minimal() + 
    geom_point(aes(color = totals_all_time$Pop_Better)) + 
    scale_color_manual(values = c("#FF3366","#00BFFF",'#9966CC')) + 
    labs(x = "Gold Medal Rank - Pop Adjusted", y = "Normal Gold Medal Rank", title = "Pop Adjusted Rank by Normal Rank",
         subtitle  =  "Superpowers Fall",color = 'Rank Type') + 
    theme(legend.position = "bottom") + 
    geom_text_repel(aes(label  =  Country),
              color  =  "gray20", size  =  1.9) + 
    scale_x_continuous(limits = c(0,35)) + 
    scale_y_continuous(limits = c(0,35)) + 
    geom_abline(linetype  =  "dashed") + 
    annotate("text", x = 3, y = 33,label  =  c("Better Ranking \nAdjusted for Pop"), size  =  4, color  =  "#00BFFF") + 
    annotate("text", x = 33, y = 3,label  =  c("Worse Ranking \nAdjusted for Pop"), size  =  4, color  =  "#9966CC")

plot6
```

## Question 3: Host Country Advantage

### Setting up data set

```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
# scrape wikipedia
wiki_hosts <- read_html("https://en.wikipedia.org/wiki/List_of_Olympic_Games_host_cities")
hosts <- html_table(html_nodes(wiki_hosts, "table")[[2]], fill = TRUE)[-1]
winter_hosts <- hosts %>% 
  filter(Winter !=  "", Year <= '2016') %>%
  rename(Host_City  =  City) %>%
  rename(Host_Country  =  Country) %>%  
  select(Host_City, Host_Country, Year)

#winter_hosts
all_with_host <- all_data %>%
  left_join(winter_hosts, by  =  'Year')

all_with_host$host_nationality_flag[all_with_host$Host_Country  ==  all_with_host$Country] <- "Host"
all_with_host$host_nationality_flag[all_with_host$Host_Country !=  all_with_host$Country] <- "Not_Host"
```

### Visualizing the Advantage/Disadvantage

Of the hosting countries, 6 have a higher average medals per Olympics hosted, than not hosted. Some countries appear to have more of an advantage when hosting. Conversely,  only 3 seem to have a hosting disadvantage: Austria, Switzerland, and Germany.
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
# hosting_averages data
# get host country avg
hosting_averages <- all_with_host %>%
  filter(Medal %in% c("Gold",'Silver','Bronze')) %>% 
  filter(Country %in% winter_hosts$Host_Country) %>%
    group_by(Country,host_nationality_flag) %>%
    summarise(Average_Medals_Per_Olympics  =  n_distinct(Games, Year, Season, Medal, Event, Country)/ n_distinct(Games,Year,Country)) %>%
  arrange(Country)

data <- hosting_averages %>%
  spread(key  =  host_nationality_flag, value  =  Average_Medals_Per_Olympics) %>%
  arrange(Not_Host)

# get differnce values for host/non-host
data$Difference <- round(data$Host -  data$Not_Host,2)
data$Positive_Color <- case_when(data$Difference < 0 ~ "#9966CC",
                                        data$Difference >0 ~"#00BFFF")
data$Positive <- case_when(data$Difference < 0 ~ 0,
                                        data$Difference >0 ~ 1)

hosting_averages <- hosting_averages %>%
  left_join(data, by  =  'Country')



plot7 <- ggplot()  + 
    theme_minimal()  + 
    geom_point(data = hosting_averages, 
               aes(y = reorder(Country,Difference)
                   , x = Average_Medals_Per_Olympics, fill = host_nationality_flag),
               size = 6, shape = 21, color = "grey30")  + 
    geom_segment(data = data, 
                 aes(y = fct_reorder2(Country,Not_Host,Positive), yend = fct_reorder2(Country,Not_Host,Positive)
                     , x = Not_Host, xend = Host,color = Positive_Color),
                 size = 1.8,
                 lineend = "butt", linejoin = "mitre",
                 arrow = arrow(length  =  unit(0.01, "npc"), type = "closed"))  + 
    scale_color_identity()  + 
    scale_fill_manual(values = c("#F1C935","#C0C0C0"),labels  =  c("Host", "Not Host")) + 
    labs(x = "Average Medals Per Olympics", y = NULL, title = "Average Medals per Olympics by Hosting Status",fill = 'Hosting Status') + 
    geom_rect(data, mapping  =  aes(xmin = 21, xmax = 25, ymin = -Inf, ymax = Inf),fill = "light blue")  + 
    geom_text(data, mapping  =  aes(label = Difference, y = Country, x = 23), size = 3)  + 
    geom_text(data = filter(data, Country == "Canada"), 
            mapping  =  aes(x = 23, y = Country, label = "Difference"),
                          size = 3.1, vjust = -2, fontface = "bold")  + 
    scale_x_continuous(limits = c(0, 25))  + 
    scale_y_discrete(expand = c(0.14,0))

plot7
```



## Question 4: Most Successful Athletes

The graph shows the total medals earned by the 20 most successful winter athletes by the total numbers of medals won.
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#all_data
successful <- all_data %>%
  filter(Medal %in% c("Gold",'Silver','Bronze')) %>%
  group_by(ID, Name, Sex) %>%
  summarise(Medal_Count  =  n_distinct(Sport,Event,Sex,Medal,Year)) %>%
  arrange(desc(Medal_Count)) %>%
  head(20)

successful
  
plot7 <- ggplot(data = successful, aes(x = Medal_Count, y = reorder(reorder(Name,Sex), Medal_Count, sum), fill = factor(Sex)))  + 
  theme_minimal() + 
  labs(fill  =  "Sex")  + 
  labs(x = "Medal Count", y = "Athlete", title = "Top 20 Most Successful Athletes")  + 
  geom_bar(stat = "identity")  + 
  scale_fill_manual(values = c('#FF82AB','#00BFFF')) + 
  theme(plot.title = element_text(hjust  =  0.5))
  
plot7
```

The graph shows the average height and weight of Olympic athletes who won medals, grouped by Sex.
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}

athlete_dimensions <- all_data %>%
  filter(Medal %in% c("Gold",'Silver','Bronze'),!is.na(Height), !is.na(Weight)) %>%
    distinct(Name, Sport,Sex,Height, Weight)

ave_dimensions <- athlete_dimensions %>%
    group_by(Sport,Sex) %>%
      summarise(Avg_Height  =  mean(Height), Ave_Weight  =  mean(Weight))

plot8 <- ggplot(data = ave_dimensions, aes(x = Avg_Height, y = Ave_Weight, color  = Sex))  + 
  scale_color_manual(values = c('#FF82AB','#00BFFF')) +
  theme_minimal() + 
  labs(x = "Average Height(cm)", y = "Average Weight", title = "Average Height and Weight of Medal Winners per Sport")  + 
  geom_point()  + 
  theme(plot.title = element_text(hjust  =  0.5)) + 
    geom_text_repel(aes(label  =  Sport),
              color  =  "gray20", size  =  1.9)

plot8

```



## Question 5: Interactive Graphs

#### Use ggplotly to make the Number of Medals per Year graph interactive
This initial graph is much improved upon when made interactive. A user can now more interpret the informatiopn by hovering over data points and clicking on the countries to tell which is which.
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
ggplotly(plot1)
```


#### Use plot_ly to make the Average Height and Weight graph interactive
This interactive version allows the user to hover on the point and see the exact statistics as well as the exact sport the point belongs to without overcrowding the plot with labels.
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
athlete_dimensions <- all_data %>%
  filter(Medal %in% c("Gold",'Silver','Bronze'), !is.na(Height), !is.na(Weight)) %>%
    distinct(Name, Sport,Sex, Height, Weight)

ave_dimensions <- athlete_dimensions %>%
    group_by(Sport, Sex) %>%
      summarise(Avg_Height  =  mean(Height), Ave_Weight  =  mean(Weight))

plot9  =  plot_ly(ave_dimensions, x = ~Avg_Height, y = ~Ave_Weight, color = ~Sex, colors  =  c("#FF82AB", "#00BFFF"), 
                type  =  "scatter", mode = 'markers', text  =  ~paste('Sport: ', Sport)) %>% 
  layout(title  =  'Average Height and Weight of Olympic Medal Winners per Sport')


plot9

```


## Question 6: add data table
```{r, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}

table_data <- all_data %>%
    filter(Medal %in% c("Gold",'Silver','Bronze'), !is.na(GDP.per.Capita)) %>% 
    group_by(Country,Medal, GDP.per.Capita, Population) %>%
    summarise(Medal_Count  =  n_distinct(Games, Year, Season, Medal, Event, Country),
              Athlete_Count  =  n_distinct(Name)) %>%
    arrange((Country)) 

datatable(totals_all_time, rownames  =  FALSE, filter  =  list(position  =  "top"), 
          options  =  list(language  =  list(sSearch  =  "Filter:")))
```
