---
title: "Billboard Charts Data"
author: "Adrian Varallyay"
date: '2022-04-20'
always_allow_html: yes
output:
  html_document:
    keep_md: yes
  pdf_document: default
font-family: Helvetica
autosize: yes
---

```{r setup, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# set up and libraries
require(knitr)
require(readr)
require(magrittr)
require(tidyverse)
require(shiny)
require(ggplot2)
require(plotly)
require(ggbump)
require(ggthemes)
require(tm)
require(stats)
require(purrr)
require(DT)

```

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# read in data
af <- read_csv("Data/audio_features.csv")
bb <-read_csv("Data/billboard.csv")
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# df for shiny slider with year
bb_year <- bb

# function to keep last n characters
keep_chr <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}
# keep last 2 chr (year digits)
bb_year$year <- keep_chr(bb_year$week_id, 2)
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# list of completed dates type char
n <- c("1958", "1959", "1960", "1961", "1962", "1963", "1964",
       "1965", "1966", "1967", "1968", "1969", "1970", "1971",
       "1972", "1973", "1974", "1975", "1976", "1977","1978",
       "1979", "1980", "1981", "1982", "1983", "1984", "1985",
       "1986", "1987", "1988", "1989", "1990", "1991", "1992", 
       "1993", "1994", "1995", "1996", "1997", "1998", "1999")

# create negate %in% object
`%notin%` <- Negate(`%in%`)
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
#Q1
# complete year format turn into double (add prefix 19 0r 20)
bb_year$year <- ifelse(bb_year$year >=58 & bb_year$year <=99, paste0("19", bb_year$year), bb_year$year)
bb_year$year <- ifelse(bb_year$year %notin% n, paste0("20", bb_year$year), bb_year$year)
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# date object for max/min
bb_year$date <- as.Date(paste0(bb_year$year, "/", substring(bb_year$week_id, 1, nchar(bb_year$week_id)-3)))
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# select columns, organize, rename 
bb_year.f <- bb_year %>%
  arrange(desc(weeks_on_chart)) %>%
  rename(most_recent_year_on_chart = year)

# keep single instance of songs 
bb_year.f <- bb_year.f[!duplicated(bb_year.f$song),]

# create song numbering
bb_year.f <- bb_year.f %>%
  mutate(rank = row_number()) %>%
  select(performer, song, rank, peak_position, weeks_on_chart, most_recent_year_on_chart)

```

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
#Q2
# number each artist song for slider selection in shiny app 2
# get number_of_songs per artist
bb_search.f <- bb_year %>%
  group_by(performer, song) %>%
  summarize() %>%
  group_by(performer) %>%
  mutate(
    artist_song_number = row_number()
  ) %>%
  mutate(
    number_of_songs = max(artist_song_number)
  )
 
#merge into final df  
bb_search.f  <- left_join(bb_year, bb_search.f, by = c("performer" = "performer",
                                                       "song" = "song"), keep = FALSE)

bb_search.f  <- bb_search.f %>%
  rename(`Song Title(s)` = song)
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# Q3
# dfs for shiny3
# audio features
af_features <- af %>%
  select(performer, song, spotify_genre, spotify_track_duration_ms, 
         instrumentalness, energy, loudness, speechiness, tempo, time_signature, 
         spotify_track_popularity) %>%
  na.omit()

# billboard top 20 peak positions
bb_features.f <-  bb_search.f %>%
  select(performer, `Song Title(s)`, date, year, peak_position ) %>%
  na.omit() %>%
  subset(peak_position <= 20)

bb_features.f$chart_ranking <- "Top 20"
bb_features.f$chart_ranking <- ifelse(bb_features.f$peak_position <= 10, "Top 10", bb_features.f$chart_ranking)
bb_features.f$chart_ranking <- ifelse(bb_features.f$peak_position <= 5, "Top 5", bb_features.f$chart_ranking)

# merge
bb_spot.f <- left_join(af_features, bb_features.f, by = c("performer" ="performer",
                                            "song" = "Song Title(s)"), keep = FALSE)

```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# keep single instance of songs 
bb_spot.f <- bb_spot.f[!duplicated(bb_spot.f$song),] %>%
  na.omit()

# clean up genre
bb_spot.f$genres <- gsub("(\\['|\\'])", "", bb_spot.f$spotify_genre) %>%
  str_split("', '")

# turn empty lists into Misc category
bb_spot.f$genres <- ifelse(bb_spot.f$genres == "[]", "Miscellaneous", bb_spot.f$genres)

# extract first element from sublist (first listed genre)
bb_spot.f$genre_simple <- map(bb_spot.f$genres, 1)

```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# apologies but I could not get this function to work
#funct to clean genre categories
#clean_genre <- function (df, genre_in, genre_out) {
  #cg <- df
  
  #for (i in genre_in) {
    #cg <- ifelse((str_detect(cg, genre_in)) == TRUE,
         #genre_out, cg) }
    
  #return(cg)
  #}

# works on single instances but not multiple entries
#bb_spot.f$genre_clean <- clean_genre(bb_spot.f$genre_simple, "metal", "Metal")
#comedy <- c("comedy", "comic", "novelty")
#bb_spot.f$genre_simple <- clean_genre(bb_spot.f$genre_simple, comedy, "Comedy")
#sort(unique(unlist(bb_spot.f$genre_simple)))
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# simplify and recategorize genres for easier UX
# children
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "'nursery")) == TRUE,
                                 "Children's Music", bb_spot.f$genre_simple)

# metal
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "metal")) == TRUE,
                                 "Metal", bb_spot.f$genre_simple)

# comedy
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "comedy")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "comic")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "novelty")) == TRUE,
                                 "Comedy", bb_spot.f$genre_simple)

# latin
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "latin" )) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple,"norteno")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple,"miami")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple,"mambo")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple,"colombian")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple,"bossa")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple,"bachata")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple,"banda")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple,"freestyle")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple,"boogaloo")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple,"bolero")) == TRUE,
                                 "Latin", bb_spot.f$genre_simple)

# religious
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "gospel")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "ccm")) == TRUE,
                                 "Religious", bb_spot.f$genre_simple)

# jazz
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "jazz")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "big band")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "brass band")) == TRUE,
                                 "Jazz", bb_spot.f$genre_simple)

# country
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "country")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "nashville sound")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "cowboy western")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "dixieland")) == TRUE,
                                 "Country", bb_spot.f$genre_simple)

# reggae                                 
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "reggae")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "dub")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "dancehall")) == TRUE,
                                 "Reggae", bb_spot.f$genre_simple)

# folk
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "folk")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "sevdah")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "lilith")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "neo-singer-songwriter")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "irish singer-songwriter")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "celtic")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "canadian celtic")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "canadian singer-songwriter")) == TRUE,
                                 "Folk", bb_spot.f$genre_simple)

# emo
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "emo")) == TRUE,
                                 "Emo", bb_spot.f$genre_simple)

# indie
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "indie")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "c86")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "deep new americana")) == TRUE,
                                 "Indie", bb_spot.f$genre_simple)

# punk
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "punk")) == TRUE,
                                 "Punk", bb_spot.f$genre_simple)

# trap
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "trap")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "brooklyn drill")) == TRUE,
                                 "Trap", bb_spot.f$genre_simple)

# house
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "house")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "bassline")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "big room")) == TRUE,
                                 "House", bb_spot.f$genre_simple)

# hip hop
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "hip hop")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "k-hop")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "bounce")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "bmore")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "crunk")) == TRUE,
                                 "Hip Hop", bb_spot.f$genre_simple)

# r&b 
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "r&b")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "quiet storm")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "rhythm and blues")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "rare groove")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "afrobeat")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "escape room")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "new jack swing")) == TRUE,
                                 "R&B", bb_spot.f$genre_simple)

# blues
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "blues")) == TRUE,
                                 "Blues", bb_spot.f$genre_simple)

# rap
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "rap")) == TRUE,
                                 "Rap", bb_spot.f$genre_simple)

# classical 
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "classical")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "orchestra")) == TRUE,
                                 "Classical", bb_spot.f$genre_simple)

# soundtrack 
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "soundtrack")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "theme")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "hollywood")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "movie tunes")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "broadway")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "scorecore")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "disney")) == TRUE,
                                 "Soundtrack", bb_spot.f$genre_simple)

# instrumental 
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "instrumental")) == TRUE | 
                                   (str_detect(bb_spot.f$genre_simple, "moog")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "jam band")) == TRUE,
                                 "Instrumental", bb_spot.f$genre_simple)

# soul
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "soul")) == TRUE,
                                 "Soul", bb_spot.f$genre_simple)

# funk
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "funk")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "minneapolis sound")) == TRUE,
                                 "Funk", bb_spot.f$genre_simple)

# pop 
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "pop")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "boy band")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "idol")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "deep talent show")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "australian talent show")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "deep adult standards")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "adult standards")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "classic schlager")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "girl group")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "beach music")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "girl band")) == TRUE,
                                 "Pop", bb_spot.f$genre_simple)

# rock
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "rock")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "surf")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "permanent wave")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "new romantic")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "alt z")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "neo mellow")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "mellow gold")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "merseybeat")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "e6fi")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "british invasion")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "new wave")) == TRUE,
                                 "Rock", bb_spot.f$genre_simple)

# dance
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "dance")) == TRUE,
                                 "Dance", bb_spot.f$genre_simple)

# disco
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "disco")) == TRUE|
                                   (str_detect(bb_spot.f$genre_simple, "hi-nrg")) == TRUE,
                                 "Disco", bb_spot.f$genre_simple)

# edm
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "edm")) == TRUE,
                                 "EDM", bb_spot.f$genre_simple)

# electro
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "complextro")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "electronica")) == TRUE|
                                   (str_detect(bb_spot.f$genre_simple, "brostep")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "downtempo")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "big beat")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "electro")) == TRUE,
                                 "Electronic", bb_spot.f$genre_simple)

# misc
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "asmr")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "background music")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "hammond organ")) == TRUE,
                                 "Miscellaneous", bb_spot.f$genre_simple)

# lofi
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "lo-fi beats")) == TRUE,
                                 "Lo-Fi", bb_spot.f$genre_simple)

# easy listening
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "easy listening")) == TRUE,
                                 "Easy Listening", bb_spot.f$genre_simple)

# drum and bass 
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "drum and bass")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "broken beat")) == TRUE,
                                 "Drum and Bass", bb_spot.f$genre_simple)

# motown
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "motown")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "doo-wop")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "bebop")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "Deep Motown")) == TRUE,
                                 "Motown", bb_spot.f$genre_simple)

# vocal
bb_spot.f$genre_simple <- ifelse((str_detect(bb_spot.f$genre_simple, "glee club")) == TRUE |
                                   (str_detect(bb_spot.f$genre_simple, "a cappella")) == TRUE,
                                 "Vocal", bb_spot.f$genre_simple)


```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# unlist genre
bb_spot.f$genre_clean <- unlist(bb_spot.f$genre_simple)

# rename col
bb_spot.f <- bb_spot.f %>%
  rename(Artist = performer,
         Song = song,
         Genre = genre_clean,
         `Time Signature` = time_signature,
         Date = date,
         `Peak Position` = peak_position,
         `Spotify Track Popularity` = spotify_track_popularity,
         Year = year)

# log instrumental for plot
bb_spot.f$`Instrumentalness (logged)` <- log(bb_spot.f$instrumentalness)

bb_spot.f$`Chart Ranking` <-  factor(bb_spot.f$chart_ranking, levels = c("Top 5","Top 10", "Top 20"),
                                     labels = c("Top 5","Top 10", "Top 20"))

```



```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# headers for shiny 1, 2 & 3
pretty_headers <-
  gsub("[_]", " ", colnames(bb_year.f)) %>%
  str_to_title()

pretty_headers2 <-
  gsub("[_]", " ", colnames(bb_search.f)) %>%
  str_to_title()

pretty_headers3 <-
  gsub("[_]", " ", colnames(bb_spot.f)) %>%
  str_to_title()
```


```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# list of artist and ranking for drop downs 
artist <- c(" ", unique(bb_search.f$performer))
artist2 <- c(" ", unique(bb_spot.f$Artist))
ranking <- c(" ", unique(bb_features.f$chart_ranking))
ranking2 <- c(unique(bb_spot.f$`Chart Ranking`))
genre_lst <- c(" ",sort(unique(unlist(bb_spot.f$genre_simple))))

```


### 1. Top Songs

Interactive datatable with the Top 20 songs (ranked by total weeks on the billboard Top 100) along with their artists, their peak billboard position, and the total weeks they were on the Billboard Top 100. Year range is selected with slider, and user can utilize datatable search and filtering functions.
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
#shiny q1
ui <- fluidPage(
  titlePanel("Artist's Billboard Top 20 Songs"),
  h4("by Weeks on Chart"),
  sidebarLayout(
    sidebarPanel(
      # slider for year range
      sliderInput(inputId = "range",
                  label = h3("Select Year Range:"),
                  min = min(as.numeric(bb_year.f$most_recent_year_on_chart)),
                  max = max(as.numeric(bb_year.f$most_recent_year_on_chart)), 
                  value = c(1990, 2000),
                  sep = ""),
      width = 3),
    
    mainPanel(
      # datatable output
      dataTableOutput("DT")
      )
    ))


server <- function(input, output) {
  #reactive object for filtering df
  sliderValues <- reactive({
    
    DT::datatable(
    rownames = FALSE,
    colnames = pretty_headers,
    (bb_year.f %>%
      filter(most_recent_year_on_chart >= input$range[1],
             most_recent_year_on_chart <= input$range[2]) %>%
       arrange(desc(weeks_on_chart)) %>%
       mutate(react_rank = row_number()) %>%
       filter(react_rank <= 20) %>%
       select(performer, song, rank, peak_position, weeks_on_chart, most_recent_year_on_chart)))
  })
  # render DT
  output$DT <- renderDataTable(
    sliderValues(), options=list(pageLength = 20, scrollX=FALSE))
}

shinyApp(ui = ui, server = server)
```

### 2. Top Artists

Full text search bar to select artist to show a visualization of the billboard ranking of all songs of the artist over time. Chart position is situated on the y-axis and date on the x. The slider is used to select the number of songs to be displayed so as to allow user control of plot clutteredness/clarity. Each song for each artist were arbitrarily numbered so as to be able to input for "which songs".
```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# shiny 2
ui <- fluidPage(
  titlePanel("Artist Songs"),
  h4("by Billboard Ranking Over Time"),
  sidebarLayout(
    sidebarPanel(
      # full text search bar for artist
      selectizeInput(
        inputId = "user",
        label = h3("Search for Artist:"),
        multiple = TRUE,
        choices = artist,
        selected = " ",
        options = list(create = FALSE,
                       placeholder = "Search Artist",
                       onDropdownOpen = I("function($dropdown) {if (!this.lastQuery.length) {this.close(); this.settings.openOnFocus = true;}}"),
                       onType = I("function (str) {if (str === \"\") {this.close();}}"),
                       onItemAdd = I("function() {this.close();}")
                       )),
      # slider for which listed songs to display 
        sliderInput(inputId = "range",
                    label = h3("Choose Which Songs to Display:"),
                    min = 1,
                    max = 183,
                    value = c(1, 2),
                    sep = ""),
    width = 3),
  
  mainPanel(
    # plot ouput
    plotOutput("songs")
            ))
  )

server <- function(input, output) {
  # reactive object for filtering df
  artistvalue <- reactive({
    
    bb_search.f %>%
      filter(performer == input$user) %>%
      filter( artist_song_number >= input$range[1] & artist_song_number <= input$range[2]) %>%
      select(performer, `Song Title(s)`, artist_song_number, number_of_songs, week_id, date, week_position)
    
  })
  # render ggplot
  output$songs <- renderPlot({
    # need to change legend title still
    ggplot(artistvalue(), aes(x = date, y = week_position, group = `Song Title(s)`)) +
      ggbump::geom_bump(aes(color = `Song Title(s)`), smooth = 7, show.legend = TRUE) +
      scale_y_reverse() +
      scale_x_date(date_labels = "%m/%Y") +
      ylab("Chart Position") +
      xlab("Date") +
      geom_rangeframe() +
      theme_tufte()
    })
  }

shinyApp(ui = ui, server = server)


```


### 3. Audio Features

Multiple selection full text genre search bar, slider date range, plotly scatter plot, Full text search bar to select artist, and  "Top 5", "Top 10", "Top 20" radio buttons. Spotify track popularity (higher value = higher number) by instrumentalness (logged).

```{r, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
# shiny 3
ui <- fluidPage(
  titlePanel("Spotify Audio Features Visualization"),
  br(),
  h4("Instrumentalness by Spotify Popularity"),
  sidebarLayout(
    sidebarPanel(
      # full text search bar for genre
      selectizeInput(
        inputId = "genre",
        label = h3("Search for Genre:"),
        multiple = TRUE,
        choices = genre_lst,
        selected = "Rock",
        options = list(create = FALSE,
                       placeholder = "Search Genre",
                       onDropdownOpen = I("function($dropdown) {if (!this.lastQuery.length) {this.close(); this.settings.openOnFocus = true;}}"),
                       onType = I("function (str) {if (str === \"\") {this.close();}}"),
                       onItemAdd = I("function() {this.close();}")
                       )),
       # slider for year range
      sliderInput(inputId = "range",
                  label = h3("Select Year Range:"),
                  min = min(as.numeric(bb_spot.f$Year)),
                  max = max(as.numeric(bb_spot.f$Year)), 
                  value = c(1958, 2021),
                  sep = ""),
      # full text search bar for artist
      selectizeInput(
        inputId = "user",
        label = h3("Search for Artist:"),
        multiple = TRUE,
        choices = artist2,
        selected = "Led Zeppelin",
        options = list(create = FALSE,
                       placeholder = "Search Artist",
                       onDropdownOpen = I("function($dropdown) {if (!this.lastQuery.length) {this.close(); this.settings.openOnFocus = true;}}"),
                       onType = I("function (str) {if (str === \"\") {this.close();}}"),
                       onItemAdd = I("function() {this.close();}")
                       )),
      # Input buttons (top 5,10,20) 
      radioButtons("top", "Top of the Charts",
                   choices = sort(ranking2),
                   selected = "Top 20"),
      width = 3),
      
       mainPanel(
    # plot ouput
    plotlyOutput("plotly")
            ))
)
    

server <- function(input, output) {
  # reactive object for filtering df
  spot <- reactive({
    # req all 4 inputs
    #req(input$genre, input$range, input$user, input$top)
    
    bb_spot.f %>%
      filter(Genre == input$genre) %>%
      filter(Year >= input$range[1] & Year <= input$range[2]) %>%
      filter(Artist == input$user) %>%
      filter(`Chart Ranking` == input$top) %>%
      select(Artist, Song, Genre, Year, `Instrumentalness (logged)`, `Chart Ranking`, `Spotify Track Popularity`)
    
  })

 output$plotly <- renderPlotly({
   
   py <- ggplot(spot(), aes(x = `Instrumentalness (logged)`, y = `Spotify Track Popularity`, color = Song, 
                            `Chart Ranking` =`Chart Ranking`,
                            Artist = Artist , Song = Song, 
                            Genre = Genre, Year = Year))
   pltly <- py + geom_point() + 
     theme_tufte()
   
   ggplotly(pltly)
     
     
 })

}

shinyApp(ui = ui, server = server)

```
